
---
output:
  html_document
params:
  quantif_file : path_to_/standardized_quantification_file
  normalization : TRUE/FALSE
  keep_empty_rows : TRUE/FALSE
title:  | 
  | Quality control of
  | `r gsub(".*/","",params$quantif_file)`
---

<style type="text/css">

body{ /* Normal  */
      font-size: 12px;
  }
td {  /* Table  */
  font-size: 8px;
}
h1.title {
  font-size: 20px;
  color: #3686D5;
  font-weight:bold;
  text-align: center;
}
h1 { /* Header 1 */
  font-size: 28px;
  color: white;
  font-weight:bold;
}
div#banner {
       background-color: #3686D5; 
       width: 100%; 
}
td{ 
    font-size: 9pt;
  }
  th { 
    font-size: 9pt;
    font-weight: bold;
    background-color: #E3E3E3;
  }
@media print
{    
    .no-print, .no-print *
    {
        display: none !important;
    }
}
</style>

<script>
function saveSvgFromParentDiv(divElId, name) {
	var divSvgWrapperEl = document.getElementById(divElId);

	var svgEl = divSvgWrapperEl.firstElementChild;
  svgEl.setAttribute("xmlns", "http://www.w3.org/2000/svg");
  var svgData = svgEl.outerHTML;
  var preface = '<?xml version="1.0" standalone="no"?>\r\n';
  var svgBlob = new Blob([preface, svgData], {type:"image/svg+xml;charset=utf-8"});
  var svgUrl = URL.createObjectURL(svgBlob);
  var downloadLink = document.createElement("a");
  downloadLink.href = svgUrl;
  downloadLink.download = name;
  document.body.appendChild(downloadLink);
  downloadLink.click();
  document.body.removeChild(downloadLink);
}
</script>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE, dev = "svglite", fig.ext = ".svg")
```


```{r include=FALSE}

library(ggplot2)
theme_set(theme_bw(base_size = 11))
library(ggrepel)
library(ggdendro)
library(scico)
library(gtable)
library(grid)
library(corrplot)
library(ade4)
library(factoextra)
library(imp4p)
library(GGally)
#library(RColorBrewer)
library(gridExtra)
library(data.table)
library(knitr)
library(kableExtra)
library(svglite)

source("../../Library/quantitativeProteomics.R")
```


```{r file_import, include=FALSE}

data <- read.table(file = params$quantif_file, header=T, sep="\t")
sample_names = colnames(data)[grepl("Intensity",names(data))]
sample_names_parsed = sub("Intensity.", "", sample_names)

```


```{r delete_empty_rows}
if(params$keep_empty_rows==FALSE){
  data$na_count = apply(data[grepl("Intensity",names(data))],1,function(x) sum(is.na(x)))
  data = subset(data,data$na_count!=ncol(data[grepl("Intensity",names(data))]))
}

```


```{r colname_parsing, results='asis'}

max_lenght_sample_name = nchar(sample_names_parsed[nchar(sample_names_parsed)==max(nchar(sample_names_parsed))][1])

if (max_lenght_sample_name>15){
  #Replace sample names by numbers
  sample_numero = paste0(rep("S",length(sample_names)),as.character(1:length(sample_names)))
  setnames(data, old=as.character(sample_names),new=sample_numero)
  sample_names = sample_numero
  #Print new names
  kable(data.frame(sample_names_parsed,sample_numero),format="html",caption="Samples id") %>% kable_styling() %>% scroll_box(height = "200px")
}else{
  sample_numero = sample_names_parsed
  setnames(data, old=as.character(sample_names),new=sample_names_parsed)
  sample_names = sample_names_parsed
}
namesDF = data.frame(sample_names_parsed,sample_numero)
colnames(namesDF)=c("Sample","Id")

```


<br>
<div id="banner">
# **Raw data visualization**
</div>


</br>

```{r log_transformation}

# Compute log10 values
for (sample in sample_names){
  colname = paste0(sample,"_log")
  data[colname] <- log10(as.numeric(unlist(data[sample])))
}

# Data parsing to a data frame with a single column containing all the values to plot, and sample in an other column
log_abundance = data[,grepl("_log",names(data))]
colnames(log_abundance) = sample_names
logIntensitiesDF = melt(log_abundance)
colnames(logIntensitiesDF) = c("sample","log_intensity")

```


<div class="row">
<div class = "col-md-6">
```{r density_plot}

logIntensitiesDF$sample <- factor(logIntensitiesDF$sample, as.character(sample_names))

density <- ggplot() +
  geom_density(data = logIntensitiesDF, mapping = aes(x=log_intensity,group=sample,color=sample), na.rm = T) +
  ggtitle("Intensity distribution over all samples")+
  xlab("log(intensity)")+
  #viridis::scale_color_viridis(alpha=0.6,begin=0.1,end=0.6,discrete = T,breaks=sample_names)+
  geom_vline(aes(xintercept=median(na.omit(logIntensitiesDF$log_intensity))), linetype="dashed", size=1)+
  geom_text(mapping=aes(x=median(na.omit(logIntensitiesDF$log_intensity)), y=0, label="median"), size=6, angle=90, vjust=-0.4, hjust=0) +
  theme(plot.title = element_text(size=22),
        axis.title=element_text(size=18),
        axis.text=element_text(size=18),
        legend.text=element_text(size=16),
        legend.title=element_text(size=18))

s <- svgstring()
plot(density)
htmltools::HTML("<div id=\"svgWrapper1\" ",s(),"<a class='no-print' href=\"javascript:saveSvgFromParentDiv('svgWrapper1','Intensity distribution over all samples.svg');\" >Save figure</a></div>")
invisible(dev.off())

```
</div>
<div class = "col-md-6">
```{r boxplots}
violinPlot <- ggplot() +
    geom_violin(data = logIntensitiesDF, mapping = aes(x = factor(sample,level=sample_names), y = log_intensity, color=sample), na.rm = T) +
    geom_boxplot(data = logIntensitiesDF, mapping = aes(x = factor(sample,level=sample_names), y = log_intensity, color=sample), width = 0.5, na.rm = T) +
    ggtitle("Intensity distribution in each sample") +
    xlab("")+
    ylab("log(intensity)")+
    theme(legend.position="none", 
        plot.title=element_text(size=22),
        axis.title=element_text(size=18),
        axis.text.x=element_text(angle=90,size=18),
        axis.text.y = element_text(size=18))

s <- svgstring()
plot(violinPlot)
htmltools::HTML("<div id=\"svgWrapper2\" ",s(),"<a class='no-print' href=\"javascript:saveSvgFromParentDiv('svgWrapper2','Intensity distribution in each sample.svg');\" >Save figure</a></div>")
invisible(dev.off())

```
</div>
</div>

<br/>

<div class="row">
<div class = "col-md-6">

```{r correlation_plot, fig.cap="Correlation coefficient were computed with pearson method."}
if (length(sample_names)<16 & nrow(data)<5000){
  correlogram = ggpairs(log_abundance,title="Sample correlation",upper=list(continuous=wrap("cor",size=2.5)))
}else{
  cormat <- round(cor(log_abundance,use = "complete.obs"),2)
  cormat = melt(cormat)
  colnames(cormat) = c("Samples1","Samples2","Coefficient")
  correlogram = ggplot(data = cormat, aes(x=Samples1, y=Samples2, fill=Coefficient)) + 
    geom_tile() +
    scale_fill_gradient2(low = "dodgerblue", mid = "white",high = "red", midpoint = 0.55) +
    xlab("")+
    ylab("")+
    ggtitle("Sample correlation") +
    theme(plot.title=element_text(size=22),
        axis.title=element_text(size=18),
        axis.text.y=element_text(size=18),
        axis.text.x=element_text(angle=90,size=18),
        legend.title=element_text("Correlation coefficient",size=16),
        legend.text = element_text(size=16))
}

s <- svgstring()
correlogram
htmltools::HTML("<div id=\"svgWrapper3\" ",s(),"<a class='no-print' href=\"javascript:saveSvgFromParentDiv('svgWrapper3','Sample correlation.svg');\" >Save figure</a></div>")
invisible(dev.off())
```
</div>

<div class = "col-md-6">

```{r identification_type_plot}

# Extract data
identification_type = data[,grepl("Identification.type.",names(data))]

if(length(identification_type)>0){
  
  # Formating data into df for ploting
  identifications = c()
  samples = c()
  for(sample in colnames(identification_type)){
    sample_name = as.character(subset(namesDF,namesDF$Sample==sub(".*.type.", "", sample))$Id)
    samples = c(samples, rep(sample_name,nrow(identification_type)))
    identifications = c(identifications,as.vector(unlist(identification_type[sample])))
  }
  IdentificationTypeDF = data.frame(samples,identifications)
  IdentificationTypeDF$samples <- factor(IdentificationTypeDF$samples, as.character(namesDF$Id))
  
  # Format and order labels for ploting
  IdentificationTypeDF$identifications <- factor(IdentificationTypeDF$identifications, rev(levels(IdentificationTypeDF$identifications))) # reverse order
  levels = levels(IdentificationTypeDF$identifications) 
  levels[length(levels) + 1] <- "Not available" # add a new factor for missing values
  IdentificationTypeDF$identifications <- factor(IdentificationTypeDF$identifications, rev(levels(IdentificationTypeDF$identifications))) # reverse order
  IdentificationTypeDF$identifications <- factor(IdentificationTypeDF$identifications, levels = levels)
  IdentificationTypeDF$identifications[is.na(IdentificationTypeDF$identifications)] <- "Not available"
  IdentificationTypeDF$identifications <- factor(IdentificationTypeDF$identifications, rev(levels(IdentificationTypeDF$identifications))) # reverse order
  
  identification_type_plot = ggplot(data = IdentificationTypeDF, mapping = aes(x=samples, fill = identifications, col=identifications)) +
  geom_bar(alpha=0.8,width=1) +
  xlab("")+
  scale_fill_manual("",values=c("By MS/MS"="dodgerblue4","By matching"="dodgerblue1","Not available"="gray70"))+
  scale_colour_manual("",values=c("By MS/MS"="dodgerblue4","By matching"="dodgerblue1","Not available"="gray70"))+
  ggtitle("Identification types distribution accross samples") +
   theme(plot.title = element_text(size=22),
        axis.title=element_text(size=18),
        axis.text.x=element_text(angle=90,size=18),
        axis.text.y=element_text(size=18),
        legend.text=element_text(size=16))
  
}

s <- svgstring()
identification_type_plot
htmltools::HTML("<div id=\"svgWrapper4\" ",s(),"<a class='no-print' href=\"javascript:saveSvgFromParentDiv('svgWrapper4','Identification types distribution accross samples.svg');\" >Save figure</a></div>")
invisible(dev.off())
```

</div>
</div>

<br>
<div id="banner">
# **Normalization**
</div>
<br>

```{r normalization}

na_count_by_sample = fast_apply_nb_na(as.matrix(data[,sample_names]),2)
na_by_sample = data.frame(na_count_by_sample,sample_names)

# Extract raw intensities
raw_abundance = data[sample_names]

if (params$normalization){
  
  # Find the sample with less NA
  reference_sample = subset(na_by_sample,na_by_sample$na_count_by_sample==min(na_by_sample$na_count_by_sample))$sample_names[1]
  
  # Normalization
  intensities_to_normalize = cbind(data$Id,raw_abundance)
  colnames(intensities_to_normalize)[1] = "Id"
  normalized_abundance = normalize(intensities_to_normalize,reference_sample)
  data = cbind(data,normalized_abundance[,-1])
  
  pattern = "_norm"
  
}else{
  
  pattern = ""
}

```


<div class="row">
<div class = "col-md-6">

```{r plot_ratios, messages=FALSE, results='asis'}

if(params$normalization){
  ratiosDF = normalized_abundance[,grepl("_ratio_",names(normalized_abundance))]
  ratiosDF = data.table::melt.data.table(data.table(ratiosDF))
  colnames(ratiosDF) = c("samples","ratio")
  
  ratiosDF$sample <- factor(sub("_ratio_.*","",ratiosDF$sample), as.character(sample_names))
  
  ratioPlot <- ggplot() +
    geom_boxplot(data = ratiosDF, mapping = aes(x=factor(samples,level=unique(samples)), y=log2(ratio),color=samples), na.rm = T) +
    ggtitle("Ratio distribution for each sample")+
    #viridis::scale_color_viridis(alpha=0.6,begin=0.1,end=0.6,discrete = T)+
    ylab("log2(ratio)") +
    xlab("") +
    theme(legend.position="none",
        plot.title=element_text(size=20),
        axis.title=element_text(size=18),
        axis.text.x=element_text(angle=90,size=18),
        axis.text.y=element_text(size=18))
  
  s <- svgstring()
  plot(ratioPlot)
  cat(htmltools::HTML("<div id=\"svgWrapper5\" ",s(),"<a class='no-print' href=\"javascript:saveSvgFromParentDiv('svgWrapper5','Ratio distribution for each sample.svg');\" >Save figure</a></div>"))
  invisible(dev.off())
}

```
</div>
</div>

<br>

<div class="row">
<div class = "col-md-6">
```{r plot_normalized_abundance, results='asis'}

if (params$normalization){

  # Plot
  normalized_abundance = normalized_abundance[grepl("_norm",names(normalized_abundance))]
  normDF = melt(normalized_abundance)
  colnames(normDF) = c("sample","intensity")
  normDF$sample = sub("_norm","",normDF$sample)
  
  median = log10(median(normDF$intensity,na.rm = T))
  
  normDF$sample <- factor(normDF$sample, as.character(sample_names))
  
  densityPlot <- ggplot(normDF) +
    geom_density(mapping = aes(x=log10(intensity),group=sample,color=sample), na.rm = T) +
    ggtitle("Intensity distribution over all samples after normalization")+
    xlab("intensity")+
    #viridis::scale_color_viridis(alpha=0.6,begin=0.1,end=0.6,discrete=T,breaks=sample_names)+
    #geom_vline(aes(xintercept=median), linetype="dashed", size=1)+
    #geom_text(mapping=aes(x=median, y=0, label="median"), size=4, angle=90, vjust=-0.4, hjust=0) +
    theme(plot.title = element_text(size=20),
          axis.title=element_text(size=18),
          axis.text=element_text(size=18),
          legend.title = element_text(size=16),
          legend.text=element_text(size=16))
  
  s <- svgstring()
  plot(densityPlot)
  cat(htmltools::HTML("<div id=\"svgWrapper6\" ",s(),"<a class='no-print' href=\"javascript:saveSvgFromParentDiv('svgWrapper6','Intensity distribution over all samples after normalization.svg');\" >Save figure</a></div>"))
  invisible(dev.off())
  
}

```
</div>

<div class = "col-md-6">

```{r boxplots_after_normalization, results='asis'}

if (params$normalization){

  bxPlot <- ggplot(normDF) +
    geom_boxplot(mapping = aes(x=sample,y=log10(intensity),color=sample), na.rm = T) +
    ggtitle("Intensity distribution in each sample after normalization")+
    xlab("")+
    #viridis::scale_color_viridis(alpha=0.6,begin=0.1,end=0.6,discrete=T,breaks=sample_names)+
    #geom_vline(aes(xintercept=median), linetype="dashed", size=1)+
    #geom_text(mapping=aes(x=median, y=0, label="median"), size=4, angle=90, vjust=-0.4, hjust=0) +
    theme(plot.title = element_text(size=20),
          axis.title=element_text(size=18),
          axis.text=element_text(size=18),
          axis.text.x=element_text(angle=90,size=18),
          legend.position="none")
  
  s <- svgstring()
  plot(bxPlot)
  cat(htmltools::HTML("<div id=\"svgWrapper6bis\" ",s(),"<a class='no-print' href=\"javascript:saveSvgFromParentDiv('svgWrapper6bis','Intensity distribution in each sample after normalization.svg');\" >Save figure</a></div>"))
  invisible(dev.off())
  
}


```


</div>
</div>


```{r normalization_legend, results='asis'}

if (params$normalization){
  cat(text_spec("\n Normalization method : each intensity is expressed relatively to a reference intensity, as a ratio of intensities. Intensities of the sample with the lowest number of missing values are used as reference intensities. Intensities are then centered by substracting the median of the ratios for each sample.",italic=T,font_size="12px"))
}else{
  cat(text_spec("Intensities were not normalized.",italic=T,font_size="12px"))
}

```


<br/>
<div id="banner">
# **Missing values imputation**
</div>
<br/>

<div class="row">
<div class = "col-md-6">
```{r na_count_by_sample, echo=FALSE}
barPlot <-ggplot(data=na_by_sample) +
  geom_bar(stat="identity",aes(x=factor(sample_names,level=sample_names), y=na_count_by_sample,fill=sample_names))+
  scale_y_continuous(name = expression("Count"), sec.axis = sec_axis(~ . * 1/nrow(data) *100 , name = "Frenquency (%)"))+
  #viridis::scale_fill_viridis(alpha=0.6,begin=0.1,end=0.6,discrete = T)+
  ggtitle("Missing values distribution accross samples") +
  ylab("Count")+
  xlab("")+
  theme(legend.position="none",
        plot.title = element_text(size=22),
        axis.title=element_text(size=18),
        axis.text=element_text(size=18),
        axis.text.x=element_text(angle=90))

s <- svgstring()
plot(barPlot)
htmltools::HTML("<div id=\"svgWrapper7\" ",s(),"<a href=\"javascript:saveSvgFromParentDiv('svgWrapper7','Missing values distribution accross samples.svg');\" >Save figure</a></div>")
invisible(dev.off())
```
</div>

<div class = "col-md-6">
```{r na_count_by_protein, echo=FALSE}
na_count_by_protein <- apply(log_abundance, 1, function(x) sum(is.na(x)))

barPlot <- ggplot() +
  aes(na_count_by_protein)+
  geom_histogram(binwidth=0.5, fill="dodgerblue3",alpha=0.6)+
  ggtitle("Missing values distribution accross proteins") +
  ylab("NA count by proteins")+
  xlab("Number of NA values")+
  scale_y_continuous(name = expression("Number of proteins"), sec.axis = sec_axis(~ . * 1/nrow(data) * 100 , name = "Frenquency (%)"))+
  theme(plot.title = element_text(size=22),
        axis.title=element_text(size=18),
        axis.text=element_text(size=18))

s <- svgstring()
plot(barPlot)
htmltools::HTML("<div id=\"svgWrapper8\" ",s(),"<a class='no-print' href=\"javascript:saveSvgFromParentDiv('svgWrapper8','Missing values distribution accross proteins.svg');\" >Save figure</a></div>")
invisible(dev.off())

```
</div>
</div>

<br>

<div class="row">
<div class = "col-md-6">
```{r missing_values_imputation, results='asis'}

if(exists('normalized_abundance') && is.data.frame(get('normalized_abundance'))){
  data_to_impute = cbind.data.frame(data$Id,normalized_abundance)
}else{
  data_to_impute = cbind.data.frame(data$Id,raw_abundance)
}

imputed_samples = impute_background_noise_gaussian(data_to_impute)[[3]]
data = cbind(data,imputed_samples)

imputed_samples_log = imputed_samples
imputed_samples_log[,1:ncol(imputed_samples_log)] = log10(imputed_samples_log)
colnames(imputed_samples_log)[1:ncol(imputed_samples_log)] = paste0(colnames(imputed_samples_log)[1:ncol(imputed_samples_log)],"_log")
data = cbind(data,imputed_samples_log)

# Make a data frame of values to plot
imputed_abundance = data[,grepl("_imputed_log",names(data))]
imputedIntensityDF = melt(imputed_abundance)
colnames(imputedIntensityDF) = c("sample","log10_intensity")
imputedIntensityDF$sample = sub("_imputed_log","",imputedIntensityDF$sample)

## imputed?
imputed = c()
for (sample_name in sample_names){
  imputed = c(imputed,is.na(raw_abundance))
}
## final dataframe
imputedIntensityDF <- data.frame(imputedIntensityDF,imputed)


# plot
histogram <- ggplot() +
  geom_histogram(data = imputedIntensityDF, mapping = aes(x = log10_intensity, fill = imputed), alpha=0.7, bins = 100) +
  scale_fill_manual(values=c("dodgerblue3", "darkorchid4"))+
  ggtitle("Log intensities distribution with imputed values") +
  xlab("log(intensity)")+
  theme(plot.title = element_text(size=22),
        axis.title=element_text(size=18),
        axis.text=element_text(size=18),
        legend.title = element_text(size=16),
        legend.text = element_text(size=16))

s <- svgstring()
plot(histogram)
htmltools::HTML("<div id=\"svgWrapper9\" ",s(),"<a class='no-print' href=\"javascript:saveSvgFromParentDiv('svgWrapper9','Log intensities distribution with imputed values.svg');\" >Save figure</a></div>")
invisible(dev.off())

cat(text_spec("\n Missing values are imputed with the gaussian model implemented in the library.",italic=T,font_size="12px"))
```
</div>
</div>

<br>
<div id="banner">
# **Dimension reduction**
</div>
<br>

```{r echo=FALSE}
pcaInput <- imputed_abundance
colnames(pcaInput) = sub("_imputed_log","",colnames(pcaInput))
pca=dudi.pca(pcaInput,scannf = FALSE, nf = 2)

```

<div class="row">
<div class = "col-md-6">
```{r echo=FALSE}
s <- svgstring()
fviz_eig(pca,addlabels=TRUE,
         barfill="dodgerblue3",
         alpha.ind=1, 
         title="Inertia",
         ggtheme=theme(plot.title = element_text(size=22),
                       axis.title=element_text(size=18),
                       axis.text=element_text(size=18)))
htmltools::HTML("<div id=\"svgWrapper10\" ",s(),"<a class='no-print' href=\"javascript:saveSvgFromParentDiv('svgWrapper10','Inertia.svg');\" >Save figure</a></div>")
invisible(dev.off())

```
</div>
<div class = "col-md-6">
```{r echo=FALSE, warning=FALSE}

rotatedData <- pca$li
Missing_values = rep(0,length(rotatedData[,1]))
for (sample_name in sample_names){
  Missing_values <- Missing_values + is.na(data[[sample_name]])
}
rotatedData$Missing_values <- Missing_values

rotationPlot <- ggplot() +
  geom_point(data = rotatedData, mapping = aes(x = Axis1, y = Axis2, col = Missing_values), alpha = 0.5) +
  ggtitle("Projection of proteins")+
  theme(plot.title=element_text(size=22),
        axis.title=element_text(size=18),
        axis.text=element_text(size=18),
        legend.text = element_text(size=16),
        legend.title = element_text(size=16))

s <- svgstring()
plot(rotationPlot)
htmltools::HTML("<div id=\"svgWrapper11\" ",s(),"<a class='no-print' href=\"javascript:saveSvgFromParentDiv('svgWrapper11','Projection of proteins.svg');\" >Save figure</a></div>")
invisible(dev.off())

```
</div>
</div>

<br>

<div class="row">
<div class = "col-md-6">
```{r echo=FALSE, warning=FALSE, message=FALSE}

s <- svgstring()
fviz_pca_var(pca,
             col.var = "contrib",
             gradient.cols = c("black", "dodgerblue"),
             repel = TRUE,
             labelsize = 4,
             title = "Samples contribution",
             ggtheme=theme(plot.title=element_text(size=20),
                           axis.title=element_text(size=18),
                           axis.text=element_text(size=18),
                           legend.text = element_text(size=16),
                          legend.title = element_text(size=16))
             )
htmltools::HTML("<div id=\"svgWrapper12\" ",s(),"<a class='no-print' href=\"javascript:saveSvgFromParentDiv('svgWrapper12','Samples contribution.svg');\" >Save figure</a></div>")
invisible(dev.off())

```
</div>

<div class = "col-md-6">
```{r echo=FALSE, warning=FALSE}
pc1 <- pca$co[,1]
pc2 <- pca$co[,2]
contribution1 <- round(100 * pca$eig[1] / sum(pca$eig))
contribution2 <- round(100 * pca$eig[2] / sum(pca$eig))

pcaPlot <- ggplot() +
    geom_point(mapping = aes(x = pc1, y = pc2)) +
    geom_label_repel(aes(x = pc1, y = pc2, label = sample_names, col=sample_names),size=5) +
    geom_hline(yintercept=0, linetype=2) +
    geom_vline(xintercept=0,linetype=2) +
    xlab(paste0("PC1 [", contribution1, "%]")) +
    ylab(paste0("PC2 [", contribution2, "%]")) +
   ggtitle("Samples projection") +
  #viridis::scale_color_viridis(alpha=0.6,begin=0.1,end=0.6,discrete = T,breaks=sample_names)+
  theme(legend.position="none",
        plot.title = element_text(size=22),
        axis.title=element_text(size=18),
        axis.text=element_text(size=18))

s <- svgstring()
plot(pcaPlot)
htmltools::HTML("<div id=\"svgWrapper13\" ",s(),"<a class='no-print' href=\"javascript:saveSvgFromParentDiv('svgWrapper13','Samples projection.svg');\" >Save figure</a></div>")
invisible(dev.off())
```
</div>
</div>

<br>
<div id="banner">
# **Hierarchical clustering**
</div>
<br>

```{r echo=FALSE}

inputProteins = imputed_abundance
distMatrixProteins <- dist(inputProteins)
hClustProteins <- fastcluster::hclust(distMatrixProteins)

inputSamples <- t(inputProteins)
distMatrixSamples <- dist(inputSamples)
hClustSamples <- fastcluster::hclust(distMatrixSamples)

```


```{r echo=FALSE, warning=FALSE}

# Create data frame
nProteins = nrow(data)

proteinRank = c()
for (i in 1:length(sample_names)){
  proteinRank = c(proteinRank,1:nProteins)
}
heatmapDF = melt(imputed_abundance)
heatmapDF$variable = sub(paste0(pattern,"_imputed_log"),"",heatmapDF$variable)
heatmapDF = cbind(heatmapDF,proteinRank,imputed)
colnames(heatmapDF) = c("sample","log_intensity","proteinRank","imputed")

heatmapDF=subset(heatmapDF,heatmapDF$imputed==F)

# Order samples according to clustering results
orderedSamples <- sample_names[hClustSamples$order]
heatmapDF$orderedSamples <- factor(heatmapDF$sample, levels = orderedSamples)
heatmapDF$x <- as.numeric(heatmapDF$orderedSamples)

# Order proteins according to clustering results
heatmapDF$orderedProteins <- factor(heatmapDF$proteinRank, levels = hClustProteins$order)
heatmapDF$y <- as.numeric(heatmapDF$orderedProteins)

# Adjust colors
minRatio <- min(heatmapDF$log_intensity)
maxRatio <- max(heatmapDF$log_intensity)
maxabsRatio <- max(abs(heatmapDF$log_intensity))

# Make ratio plot
hcPlot <- ggplot() +
    geom_raster(data = heatmapDF, mapping = aes(x = x, y = y, fill = log_intensity)) +
    scale_fill_gradientn(colours=c("green","yellow","red")) +
    #scale_fill_scico(palette = "tokyo") +
    ggtitle("")+
    xlab("")+
    scale_x_continuous(name = "Sample", breaks = 1:length(orderedSamples), labels = orderedSamples, expand = c(0, 0)) +
    scale_y_continuous(name = "Protein", expand = c(0, 0)) +
    theme(axis.text.y = element_blank(),
          axis.ticks.y = element_blank(),
          plot.title=element_text(size=22),
          axis.title=element_text(size=18),
          axis.text=element_text(angle=90, size=14),
          legend.text=element_text(size=16),
          legend.title=element_text(size=18))
matrixGrob <- ggplotGrob(hcPlot)

# Make dendrogram plots
dendrogramSamples <- dendro_data(hClustSamples, type="rectangle")
dendrogramDataSamples <- segment(dendrogramSamples)
dendrogramSamplesPlot <- ggplot() +
    geom_segment(data = dendrogramDataSamples, mapping = aes(x=x, y=y, xend=xend, yend=yend)) +
    #scale_y_continuous(expand = c(0, 0)) +
    #scale_x_continuous(expand = c(0, 0), limits = c(0.5, 6.5)) +
    theme(axis.line = element_blank(),
          axis.ticks = element_blank(),
          axis.text = element_blank(),
          axis.title = element_blank(),
          panel.background = element_blank(),
          panel.grid = element_blank(),
          panel.border = element_blank())
dendroSampleGrob <- ggplotGrob(dendrogramSamplesPlot)

# if(nProteins<10000){
#   dendrogramProteins <- dendro_data(hClustProteins, type="rectangle")
#   dendrogramDataProteins <- segment(dendrogramProteins)
#   dendrogramProteinsPlot <- ggplot() +
#     geom_segment(data = dendrogramDataProteins, mapping = aes(x=x, y=y, xend=xend, yend=yend)) +
#     coord_flip() +
#     scale_y_reverse(expand = c(0, 0)) +
#     scale_x_continuous(expand = c(0, 0), limits = c(0.5, nProteins + 0.5)) +
#     theme(axis.line = element_blank(),
#           axis.ticks = element_blank(),
#           axis.text = element_blank(),
#           axis.title = element_blank(),
#           panel.background = element_blank(),
#           panel.grid = element_blank(),
#           panel.border = element_blank())
#   dendroProteinGrob <- ggplotGrob(dendrogramProteinsPlot)
# }

dendroSampleGrob <- gtable_add_cols(dendroSampleGrob, unit(rep(1, ncol(matrixGrob) - ncol(dendroSampleGrob)), "null"), pos = -1)
result <- rbind(dendroSampleGrob[7, ], matrixGrob[7:nrow(matrixGrob), ], size = "last")
result <- rbind(matrixGrob[1:6, ], result, size = "last")
result$heights[7] <- unit(0.2, "null")
result$widths[5] <- unit(0.2, "null")

s <- svgstring()
grid.newpage()
grid.draw(result)
htmltools::HTML("<div id=\"svgWrapper14\" ",s(),"<a class='no-print' href=\"javascript:saveSvgFromParentDiv('svgWrapper14','Heatmap.svg');\" >Save figure</a></div>")
invisible(dev.off())


```

<br>

