---
output:
  html_document
params:
  repository: "../../Results/Human_yeast/ROC/imputation/mcar"
  variants: "../../Results/Human_yeast/ROC/variants.csv"
  default_ratio_threshold: 1
  default_pval_threshold: 0.01
  min_pval: 0.001
  max_pval: 0.05
  min_ratio: 0.5
  max_ratio: 3
  nb_tests: 20
    
title: "ROC"
---

<style type="text/css">

body{ /* Normal  */
      font-size: 12px;
  }
h1.title {
  font-size: 20px;
  color: #3686D5;
  font-weight:bold;
  text-align: center;
}
h1 { /* Header 1 */
  font-size: 28px;
  color: white;
  font-weight:bold;
}
h2 { /* Header 2 */
  font-size: 20px;
  color: #3686D5;
  font-weight:bold;
}
div#banner {
       background-color: #3686D5; 
       width: 100%; 
}
td{ 
    font-size: 9pt;
}
th { 
  font-size: 9pt;
  font-weight: bold;
  background-color: white;
}
</style>

<script>
function saveSvgFromParentDiv(divElId, name) {
	var divSvgWrapperEl = document.getElementById(divElId);

	var svgEl = divSvgWrapperEl.firstElementChild;
  svgEl.setAttribute("xmlns", "http://www.w3.org/2000/svg");
  var svgData = svgEl.outerHTML;
  var preface = '<?xml version="1.0" standalone="no"?>\r\n';
  var svgBlob = new Blob([preface, svgData], {type:"image/svg+xml;charset=utf-8"});
  var svgUrl = URL.createObjectURL(svgBlob);
  var downloadLink = document.createElement("a");
  downloadLink.href = svgUrl;
  downloadLink.download = name;
  document.body.appendChild(downloadLink);
  downloadLink.click();
  document.body.removeChild(downloadLink);
}
</script>



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F,warning=F,message=F,opts.Label="kill_prefix",fig.dim=c(20,10))
```

```{r}
library(dplyr)
library(reshape2)
library(ggplot2)
library(svglite)
library(kableExtra)

source("../../Library/quantitativeProteomics.R")
```

```{r read_files}
files = list.files(path = params$repository, pattern = ".txt",full.names = T)
ldf <- lapply(files, read.delim,sep = "\t",check.names=F)
names(ldf) <- sapply(files, function(x) tail(strsplit(sub(".csv","",x),"/")[[1]],n=1))

variants = as.character(unlist(read.table(params$variants)))
```

<br>
<div id="banner">
# **Metadata**
</div>
<br> 


```{r date, results='asis'}
kable(data.frame(c("Number of files", "File names", "Date"),c(length(files),paste(names(ldf),collapse=" ; "),format(Sys.time(), '%y-%m-%d %H:%M:%S'))),format="html",col.names = NULL,booktabs = T, caption = "Analysis") %>%
          kable_styling(bootstrap_options="condensed",full_width = F,position = "left") %>%
          column_spec(1, bold = T)
```

```{r extract_statistics}

statistics_tables_notMerged_list = list()
names_statistics_tables_notMerged_list = c()
i=1

statistics_tables_merged_list = list()
j=1

for (file in names(ldf)){
  
  #######################################
  # Extract accession, ratio and pval #
 #######################################
  
  Accession = ldf[[file]]$Accession
  FC = ldf[[file]][grepl("^log2\\(FC|^zscore",colnames(ldf[[file]]))]
  qval = ldf[[file]][grepl("^qval",colnames(ldf[[file]]))]
  
  if (length(qval)<1){
    pval = ldf[[file]][grepl("^pval",colnames(ldf[[file]]))]
    statistic_data = data.frame(Accession,FC,pval,check.names=F)
  }else{
    statistic_data = data.frame(Accession,FC,qval,check.names=F)
  }
  
  ############################################################
  # Separate the different comparisons into different tables #
  ############################################################
  
  # Separate the columns according to the comparison
  DFlist <- split.default(statistic_data, gsub(".*_|\\)", "", names(statistic_data)))
  
  for(k in 1:length(DFlist)){
    
    if (!("Accession" %in% names(DFlist[[k]]))){
      table = cbind(Accession,DFlist[[k]])
      colnames(table) = c("Accession","ratio","pval")
      
      statistics_tables_notMerged_list[[i]] = table
      i=i+1
      
      names_statistics_tables_notMerged_list = c(names_statistics_tables_notMerged_list,paste0(file,"_",sub(".*_", "", names(DFlist[[k]]))[1]))
    }
  }
  
  ################################################
  # Create a global table by merging comparisons #
  ################################################
  
  # Separate the columns according to its content (ratio or pval/qval)
  DFlist <- split.default(statistic_data, sub("_.*", "", names(statistic_data)))
  
  statistic_data = data.frame(as.character(unlist(rep(DFlist[[1]],ncol(DFlist[[2]])))),melt(DFlist[[2]]),melt(DFlist[[3]])$value)
  colnames(statistic_data) = c("Accession","Comparison","ratio","pval")
  
  statistic_data$Comparison = sub(".*_","",statistic_data$Comparison)
  
  statistic_data$specificity = rep(NA,nrow(statistic_data))
  statistic_data$specificity[(abs(statistic_data$ratio) >= params$default_ratio_threshold) & (statistic_data$pval <= params$default_pval_threshold) & !(statistic_data$Accession %in% variants)] <-"FP"
  statistic_data$specificity[(abs(statistic_data$ratio) >= params$default_ratio_threshold) & (statistic_data$pval <= params$default_pval_threshold) & (statistic_data$Accession %in% variants)] <-"TP"
  statistic_data$specificity[((abs(statistic_data$ratio) < params$default_ratio_threshold) | (statistic_data$pval > params$default_pval_threshold)) & !(statistic_data$Accession %in% variants)] <-"TN"
  statistic_data$specificity[((abs(statistic_data$ratio) < params$default_ratio_threshold) | (statistic_data$pval > params$default_pval_threshold)) & (statistic_data$Accession %in% variants)] <-"FN"
  
  # Source file
  statistic_data$Source = rep(file,nrow(statistic_data))
  
  statistics_tables_merged_list[[j]] = statistic_data
  j=j+1
  
}

names(statistics_tables_merged_list) = names(ldf)
names(statistics_tables_notMerged_list) = names_statistics_tables_notMerged_list

```


<br>
<div id="banner">
# **Volcano plots**
</div>
<br>



```{r merged_volcano_plots_by_file, results='asis'}

for (file in names(statistics_tables_merged_list)){
  
  cat(text_spec(paste0(" \n ",file),bold=T,font_size=18,color="#3686D5"))
  
  statistic_data = statistics_tables_merged_list[[file]]
  
  Volcano = ggplot(statistic_data) +
  geom_point(aes(x=ratio, y=-log10(pval), colour=specificity,shape=Comparison),size=3) +
  #scale_colour_manual("",breaks=c("TP","FP","FN"),values=c("green","red","orange")) +
  scale_colour_manual("",values = c("TP" = "green","FP" = "red","FN" = "orange","TN" = "grey60")) +
  guides(colour = guide_legend(override.aes = list(shape = 15,size=5))) +
  geom_hline(yintercept=0)+
  geom_vline(xintercept=0)+
  ggtitle(paste0("Sensibility and specificity"))+
  xlab("ratio")+
  ylab('-log10(pval)')+
  theme(plot.title = element_text(size=22),
      axis.title=element_text(size=30),
      axis.text=element_text(size=30),
      legend.text=element_text(size=30),
      plot.margin = unit(c(2,0,0,0), "cm"),
      legend.title=element_text(size=30))

  
  plot(Volcano)
  
}

```



```{r merged_volcano_plots_all_file, results='asis'}

cat(text_spec(" \n All files",bold=T,font_size=18,color="#3686D5"))

global_statistic_data = bind_rows(statistics_tables_merged_list)

Volcano = ggplot(global_statistic_data, aes(x=ratio, y=-log10(pval),shape=Comparison)) +
    geom_point(size=3,col="grey60") +
    geom_point(data=subset(global_statistic_data,global_statistic_data$specificity %in% c("TP","FP")), aes(x=ratio, y=-log10(pval), colour=Source, shape=Comparison),size=3) +
    guides(colour = guide_legend(override.aes = list(shape = 15))) +
    #scale_shape_manual(breaks=unique(global_statistic_data$Comparison),values=sample(1:20,length(unique(global_statistic_data$Comparison)))) + 
    geom_hline(yintercept=0)+
    geom_vline(xintercept=0)+
    ggtitle("Merged volcano plot for all files")+
    xlab("Ratio")+
    ylab('-log10(pval)')+
    theme(plot.title = element_text(size=22),
        axis.title=element_text(size=18),
        axis.text=element_text(size=18),
        legend.text=element_text(size=18),
        plot.margin = unit(c(2,0,0,0), "cm"),
        legend.title=element_text(size=20))

  plot(Volcano)

```


<br>
<div id="banner">
# **ROC curves**
</div>
<br>

```{r parameters}

n <- params$nb_tests
ratioVar <- c(round(seq(params$min_ratio, params$max_ratio, length.out = n-1),2),params$default_ratio_threshold)
pvalVar <- c(round(seq(params$min_pval, params$max_pval, length.out = n-1),3),params$default_pval_threshold)

```



```{r individual_ROC, results='asis'}

cat(text_spec("Each comparison from each file \n \n ",bold=T,font_size=22,color="#3686D5"))

ROClist <- list()

for (file in names(statistics_tables_notMerged_list)) {
  
  cat(text_spec(file,bold=T,underline=T,font_size=18,color="black"))
  
  statistic_table = statistics_tables_notMerged_list[[file]]
  
  gtab = compute_ROC(statistic_table,n,ratioVar,pvalVar,variants)
  ROClist[[length(ROClist)+1]] <- gtab
  
  g <- ggplot(gtab, aes(x = FDP, y = Sensitivity, group = factor(ratio_threshold))) + 
    geom_hline(yintercept = 95, col = "grey") + 
    geom_vline(xintercept = 5, col = "grey") + 
    geom_line() + facet_wrap(~ratio_threshold) + 
    ggtitle("Ratio threshold effect") +
    theme(plot.title = element_text(size=22),
      strip.text.x = element_text(size = 20),
      axis.title=element_text(size=18),
      axis.text=element_text(size=18),
      legend.text=element_text(size=18),
      plot.margin = unit(c(2,0,0,0), "cm"),
      legend.title=element_text(size=20))
  
  
  plot(g)
  
  g <- ggplot(gtab, aes(x = FDP, y = Sensitivity, group = factor(pval_threshold))) + 
    geom_hline(yintercept = 95, col = "grey") + 
    geom_vline(xintercept = 5, col = "grey") + 
    geom_line() + facet_wrap(~pval_threshold) + 
    ggtitle("Pval threshold effect") +
    theme(plot.title = element_text(size=22),
      strip.text.x = element_text(size = 20),
      axis.title=element_text(size=18),
      axis.text=element_text(size=18),
      legend.text=element_text(size=18),
      plot.margin = unit(c(2,0,0,0), "cm"),
      legend.title=element_text(size=20))

  
  plot(g)
    
  g <- ggplot(gtab, aes(x = factor(pval_threshold))) + 
    theme_minimal()  + 
    theme(axis.text.x = element_text(angle = 90, hjust = 1)) + 
    stat_summary(aes(x = factor(pval_threshold), y = Sensitivity, col = "Sensitivity"),fun.y = median, fun.ymin = min, fun.ymax = max) +
    stat_summary(aes(x = factor(pval_threshold), y = FDP, col = "FDP"),fun.y = median, fun.ymin = min, fun.ymax = max) + 
    scale_colour_manual("",values = c("Sensitivity"="darkblue","FDP"="red")) +
    xlab("-log10(p-value)") + 
    ggtitle("Impact of the choice of the p-value") +
    theme(plot.title = element_text(size=22),
      axis.title=element_text(size=18),
      axis.text=element_text(size=18),
      legend.text=element_text(size=18),
      plot.margin = unit(c(2,0,0,0), "cm"),
      legend.title=element_text(size=20))
  
  
  plot(g)

  # Calculate inflexion point for the Z-score curves:
  vec <- vector(length=length(ratioVar))
  for (i in 1:length(ratioVar)) {
    sub <- gtab[gtab[,3]==ratioVar[i],]
    vec[i] <- min(sub[,1][sub[,2]>95])
  }
  
  gtab2 <- data.frame("ratio_threshold" = ratioVar, "Min_95_FDP" = vec)
  
  g <- ggplot(gtab2, aes(x = ratio_threshold, y = Min_95_FDP)) + 
    theme_minimal()  + 
    theme(axis.text.x = element_text(angle = 90, hjust = 1)) + 
    geom_smooth() + 
    ylab("Minimum FDP value with sensitivity above 95%") + 
    xlab("abs(ratio)") + 
    ggtitle("Evaluation of the impact of the ratio") +
    theme(plot.title = element_text(size=22),
      axis.title=element_text(size=18),
      axis.text=element_text(size=18),
      legend.text=element_text(size=18),
      plot.margin = unit(c(2,0,0,0), "cm"),
      legend.title=element_text(size=20))
  
  
  plot(g)

}

names(ROClist) = names(statistics_tables_notMerged_list)

```


```{r ROC_by_file, results='asis'}

if(length(ROClist)>length(ldf)){
  
  ROClist <- list()

  cat(text_spec("Merged comparisons for each file \n \n ",bold=T,font_size=22,color="#3686D5"))

  for (file in names(statistics_tables_merged_list)) {

    cat(text_spec(file,bold=T,font_size=18,underline=T,color="black"))

    statistic_table = statistics_tables_merged_list[[file]]

    gtab = compute_ROC(statistic_table,n,ratioVar,pvalVar,variants)
    ROClist[[length(ROClist)+1]] <- gtab

    g <- ggplot(gtab, aes(x = FDP, y = Sensitivity, group = factor(ratio_threshold))) +
      geom_hline(yintercept = 95, col = "grey") +
      geom_vline(xintercept = 5, col = "grey") +
      geom_line() + facet_wrap(~ratio_threshold) +
      ggtitle("Ratio threshold effect") +
      theme(plot.title = element_text(size=22),
        strip.text.x = element_text(size = 20),
        axis.title=element_text(size=18),
        axis.text=element_text(size=18),
        legend.text=element_text(size=18),
        plot.margin = unit(c(2,0,0,0), "cm"),
        legend.title=element_text(size=20))

    
    plot(g)

    g <- ggplot(gtab, aes(x = FDP, y = Sensitivity, group = factor(pval_threshold))) +
      geom_hline(yintercept = 95, col = "grey") +
      geom_vline(xintercept = 5, col = "grey") +
      geom_line() + facet_wrap(~pval_threshold) +
      ggtitle("Pval threshold effect") +
      theme(plot.title = element_text(size=22),
        strip.text.x = element_text(size = 20),
        axis.title=element_text(size=18),
        axis.text=element_text(size=18),
        legend.text=element_text(size=18),
        plot.margin = unit(c(2,0,0,0), "cm"),
        legend.title=element_text(size=20))

    plot(g)

    g <- ggplot(gtab, aes(x = factor(pval_threshold))) +
      theme_minimal()  +
      theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
      stat_summary(aes(x = factor(pval_threshold), y = Sensitivity, col = "Sensitivity"),fun.y = median, fun.ymin = min, fun.ymax = max) +
      stat_summary(aes(x = factor(pval_threshold), y = FDP, col = "FDP"),fun.y = median, fun.ymin = min, fun.ymax = max) +
      scale_colour_manual("",values = c("Sensitivity"="darkblue","FDP"="red")) +
      xlab("-log10(p-value)") +
      ggtitle("Impact of the choice of the p-value") +
      theme(plot.title = element_text(size=22),
        axis.title=element_text(size=18),
        axis.text=element_text(size=18),
        legend.text=element_text(size=18),
        plot.margin = unit(c(2,0,0,0), "cm"),
        legend.title=element_text(size=20))

    plot(g)

    # Calculate inflexion point for the Z-score curves:
    vec <- vector(length=length(ratioVar))
    for (i in 1:length(ratioVar)) {
      sub <- gtab[gtab[,3]==ratioVar[i],]
      vec[i] <- min(sub[,1][sub[,2]>95])
    }

    gtab2 <- data.frame("ratio_threshold" = ratioVar, "Min_95_FDP" = vec)

    g <- ggplot(gtab2, aes(x = ratio_threshold, y = Min_95_FDP)) +
      theme_minimal()  +
      theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
      geom_smooth() +
      ylab("Minimum FDP value with sensitivity above 95%") +
      xlab("abs(ratio)") +
      ggtitle("Evaluation of the impact of the ratio") +
      theme(plot.title = element_text(size=22),
        axis.title=element_text(size=18),
        axis.text=element_text(size=18),
        legend.text=element_text(size=18),
        plot.margin = unit(c(2,0,0,0), "cm"),
        legend.title=element_text(size=20))

    plot(g)

  }
}

```
 
```{r roc_all_files, results='asis'}

cat(text_spec(" \n Combined analysis of all files \n \n ",bold=T,font_size=22,color="#3686D5"))

names(ROClist) = names(ldf)

for (ROCfile in names(ROClist)){
  ROClist[[ROCfile]]$Source = ROCfile
}

totalROC = bind_rows(ROClist)

g <- ggplot(totalROC, aes(x = FDP, y = Sensitivity, group = Source, col = Source)) + 
  geom_hline(yintercept = 95, col = "grey") + 
  geom_vline(xintercept = 5, col = "grey") + 
  geom_line(size = 0.8) + 
  facet_wrap(~ratio_threshold) + 
  ggtitle("Ratio threshold effect")+
  theme(plot.title = element_text(size=22),
        strip.text.x = element_text(size = 20),
        axis.title=element_text(size=18),
        axis.text=element_text(size=18),
        legend.text=element_text(size=18),
        plot.margin = unit(c(2,0,0,0), "cm"),
        legend.title=element_text(size=20))

plot(g)

g <- ggplot(totalROC, aes(x = FDP, y = Sensitivity, group = Source, col = Source)) + 
  geom_hline(yintercept = 95, col = "grey") + 
  geom_vline(xintercept = 5, col = "grey") + 
  geom_line(size = 0.8) + 
  facet_wrap(~pval_threshold) + 
  ggtitle("Pval threshold effect") +
  theme(plot.title = element_text(size=22),
        strip.text.x = element_text(size = 20),
        axis.title=element_text(size=18),
        axis.text=element_text(size=18),
        legend.text=element_text(size=18),
        plot.margin = unit(c(2,0,0,0), "cm"),
        legend.title=element_text(size=20))

plot(g)

g <- ggplot(totalROC, aes(x = factor(pval_threshold, col = Source))) + 
  theme_minimal()  +
  stat_summary(aes(x = factor(pval_threshold), y = Sensitivity,col = "Sensitivity", shape = Source),fun.y = mean, fun.ymin = min, fun.ymax = max) +
  stat_summary(aes(x = factor(pval_threshold), y = FDP, col = "FDP", shape = Source),fun.y = mean, fun.ymin = min, fun.ymax = max) + 
  scale_colour_manual("",values = c("Sensitivity"="darkblue","FDP"="red")) +
  ylab("Median Sensitivity in blue, FDP in red") + 
  xlab("-log10(p-value)") + 
  ggtitle("Impact of the choice of the p-value") +
  theme(plot.title = element_text(size=22),
        axis.title=element_text(size=18),
        axis.text=element_text(size=18),
        legend.text=element_text(size=18),
        plot.margin = unit(c(2,0,0,0), "cm"),
        legend.title=element_text(size=20))

plot(g)

```


```{r final_roc_curve_pval, results='asis'}

cat(text_spec("Final ROC curve \n \n ",bold=T,font_size=22,color="#3686D5"))

gtab <- totalROC[totalROC$pval==params$default_pval_threshold,]
g <- ggplot(gtab, aes(x = FDP, y = Sensitivity, group = Source, col = Source)) + 
  geom_hline(yintercept = 0) + geom_vline(xintercept = 0) + 
  geom_line(size = 0.8) + 
  ggtitle(paste0("Final ROC curves for all files with pval=",params$default_pval_threshold)) + 
  scale_color_brewer(palette = "Set1") + 
  theme_minimal() +
  theme(plot.title = element_text(size=22),
        axis.title=element_text(size=30),
        axis.text=element_text(size=30),
        legend.text=element_text(size=30),
        plot.margin = unit(c(2,0,0,0), "cm"),
        legend.title=element_text(size=30))

s <- svgstring(width=20,height=10)
plot(g)
htmltools::HTML(paste0("<div id=\"svgWrapper5\" ",s(),"<a class='no-print' style='float:right' href=\"javascript:saveSvgFromParentDiv('svgWrapper5','Final ROC curves for all files.svg');\" >Save figure</a></div>"))
invisible(dev.off())

```


```{r final_roc_curve_ratio, results='asis'}

cat(text_spec("Final ROC curve \n \n ",bold=T,font_size=22,color="#3686D5"))

gtab <- totalROC[totalROC$ratio==params$default_ratio_threshold,]
g <- ggplot(gtab, aes(x = FDP, y = Sensitivity, group = Source, col = Source)) + 
  geom_hline(yintercept = 0) + geom_vline(xintercept = 0) + 
  geom_line(size = 0.8) + 
  ggtitle(paste0("Final ROC curves for all files with ratio=",params$default_ratio_threshold)) + 
  scale_color_brewer(palette = "Set1") + 
  xlab("Specificity") +
  theme_minimal() +
  theme(plot.title = element_text(size=30),
        axis.title=element_text(size=30),
        axis.text=element_text(size=30),
        legend.text=element_text(size=22),
        plot.margin = unit(c(2,0,0,0), "cm"),
        legend.title=element_text(size=30))

s <- svgstring(width=20,height=10)
plot(g)
htmltools::HTML(paste0("<div id=\"svgWrapper5\" ",s(),"<a class='no-print' style='float:right' href=\"javascript:saveSvgFromParentDiv('svgWrapper5','Final ROC curves for all files.svg');\" >Save figure</a></div>"))
invisible(dev.off())

```
