---
title: "CytoC"
output:
  html_document
params:
  file_name : ""
---

<style type="text/css">

body{ /* Normal  */
      font-size: 12px;
  }
h1.title {
  font-size: 20px;
  color: #3686D5;
  font-weight:bold;
  text-align: center;
}
h1 { /* Header 1 */
  font-size: 28px;
  color: white;
  font-weight:bold;
}
h2 { /* Header 2 */
  font-size: 20px;
  color: #3686D5;
  font-weight:bold;
}
div#banner {
       background-color: #3686D5; 
       width: 100%; 
}
td{ 
    font-size: 9pt;
}
th { 
  font-size: 9pt;
  font-weight: bold;
  background-color: white;
}
</style>

<script>
function saveSvgFromParentDiv(divElId, name) {
	var divSvgWrapperEl = document.getElementById(divElId);

	var svgEl = divSvgWrapperEl.firstElementChild;
  svgEl.setAttribute("xmlns", "http://www.w3.org/2000/svg");
  var svgData = svgEl.outerHTML;
  var preface = '<?xml version="1.0" standalone="no"?>\r\n';
  var svgBlob = new Blob([preface, svgData], {type:"image/svg+xml;charset=utf-8"});
  var svgUrl = URL.createObjectURL(svgBlob);
  var downloadLink = document.createElement("a");
  downloadLink.href = svgUrl;
  downloadLink.download = name;
  document.body.appendChild(downloadLink);
  downloadLink.click();
  document.body.removeChild(downloadLink);
}
</script>


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F,warning=F,message=F,opts.label="kill_prefix",fig.dim=c(20,10))
```

```{r include=FALSE}
#library("openxlsx")
library(ggplot2)
library(scales)
library(grid)
library(gridExtra)
#library(cowplot)
#library("RColorBrewer")
library(knitr)
library(kableExtra)
library(reshape)
#library(dplyr)
library(knitr)
library(svglite)
library(kableExtra)
```


```{r file_import}

#input = read.table(params$file_name,sep=",",header=T)
cytoc_ref = read.table("../../Data/CytoC/Rapport/cytoc_xics_ref.csv",sep=",",header=T)
cytoc_ref$Source = rep("reference",nrow(cytoc_ref))
cytoc_ref = cytoc_ref[order(as.Date(cytoc_ref$AcquiredTime)),] #Sort by date

cytoc_test = read.table("../../Data/CytoC/Rapport/cytoc_xics_test.csv",sep=",",header=T)
cytoc_test$Source = rep("test",nrow(cytoc_test))
cytoc_test = cytoc_test[order(as.Date(cytoc_test$AcquiredTime)),] #Sort by date

#layout = length(unique(input$AcquiredTime)) < 40
```

<br>
<div id="banner">
# Global metrics distribution comparisons
</div>
<br>

```{r compute_data}

#############
# Reference #
#############

# Extracting ppm
PPM = substring(cytoc_ref$Annotations, regexpr("delta PPM = ", cytoc_ref$Annotations) + 12)
cytoc_ref$PPM = as.numeric(PPM)

# Median centering
cytoc_ref = cytoc_ref[order(cytoc_ref$Precursor),] # Sort by precursor
centered_rt_ref = c()
medians_rt_ref = NULL
centered_intensity = c()
medians_intensity_ref = NULL
medians_ppm_ref = NULL
for (precursor in unique(cytoc_ref$Precursor)){
  sub = subset(cytoc_ref, cytoc_ref$Precursor==precursor)
  # RT
  median = median(sub$Best.RT)
  medians_rt_ref = rbind(medians_rt_ref,c(precursor,median))
  centered_rt_ref = c(centered_rt_ref, sub$Best.RT-median)
  # Intensity
  median = median(sub$TotalArea)
  medians_intensity_ref = rbind(medians_intensity_ref,c(precursor,median))
  centered_intensity = c(centered_intensity, sub$TotalArea/median)
  # ppm
  median = median(sub$PPM)
  medians_ppm_ref = rbind(medians_ppm_ref,c(precursor,median))
}
cytoc_ref$centered_rt = centered_rt_ref
cytoc_ref$centered_intensity = centered_intensity

#########
# Query #
#########

# Extracting ppm
PPM = substring(cytoc_test$Annotations, regexpr("delta PPM = ", cytoc_test$Annotations) + 12)
cytoc_test$PPM = as.numeric(PPM)

cytoc_test = cytoc_test[order(cytoc_test$Precursor),] # Sort by precursor
centered_rt_ref = c()
centered_intensity = c()
z_rt = c()
fc_intensity = c()

for (precursor in unique(cytoc_test$Precursor)){
  
  # Median centering
  sub = subset(cytoc_test, cytoc_test$Precursor==precursor)
  ## RT
  median = median(sub$Best.RT)
  centered_rt_ref = c(centered_rt_ref, sub$Best.RT-median)
  ## Intensity
  median = median(sub$TotalArea)
  centered_intensity = c(centered_intensity, sub$TotalArea/median)
  
  for (date in unique(sub$AcquiredTime)){
    sub2 = subset(sub,sub$AcquiredTime==date)
    
    # RT Z-score computing
    median_ref = as.numeric(subset(medians_rt_ref, medians_rt_ref[,1]==precursor)[,2])
    z = (sub2$Best.RT - median_ref)
    z_rt = c(z_rt,z)
    
    # intensity FC computing
    median_ref = as.numeric(subset(medians_intensity_ref, medians_intensity_ref[,1]==precursor)[,2])
    FC = sub2$TotalArea/median_ref
    fc_intensity = c(fc_intensity,FC)
  }
}
cytoc_test$centered_rt = centered_rt_ref
cytoc_test$centered_intensity = centered_intensity
cytoc_test$z_rt = z_rt
cytoc_test$FC = log2(fc_intensity)

# Group data for plots
cytoc_ref$z_rt = rep(NA,nrow(cytoc_ref))
cytoc_ref$FC = rep(NA,nrow(cytoc_ref))
cytoc_test$Source = rep("test",nrow(cytoc_test))
cytoc_ref$Source = rep("reference",nrow(cytoc_ref))
data = rbind(cytoc_test,cytoc_ref)
data = data[order(data$Source),]

```



## Retention time
<br>

```{r RT, fig.cap="RT-median"}

# Boxplots
gg2 = ggplot(data = data, aes(x = Precursor, y = centered_rt)) + 
  geom_boxplot(aes(col = Source),size=0.8)+
  ggtitle("Comparison of the distributions of \n centered RTs for each peptide")+
  ylab("Centered RT")+
  theme(axis.text.x = element_text(angle=90,size=25),
        axis.text.y=element_text(size=30),
        plot.title=element_text(size=24),
        legend.text=element_text(size=30),
        legend.title = element_text(size=30),
        axis.title=element_text(size=30))

colour = unique(ggplot_build(gg2)$data[[1]]$colour)

# Histogram
gg1 = ggplot() +
  geom_histogram(data=cytoc_test, aes(x=centered_rt),fill=colour[2],col=colour[2],alpha = 0.4)+
  geom_histogram(data=cytoc_ref, aes(x=centered_rt),fill=colour[1],col=colour[1],alpha = 0.4)+
  ggtitle("Comparison of the global distributions of centered RTs")+
  xlab("Centered RT")+
  theme(axis.text.x = element_text(angle=90,size=30),
        axis.text.y=element_text(size=30),
        plot.title=element_text(size=24),
        legend.text=element_text(size=30),
        legend.title = element_text(size=30),
        axis.title=element_text(size=30))

s <- svgstring(width=20,height=10)
grid.arrange(arrangeGrob(gg1+theme(plot.margin = unit(c(0,2,0,0), "cm"))), 
                arrangeGrob(gg2),
                ncol=2,nrow=1)
htmltools::HTML("<div id=\"svgWrapper1\" ",s(),"<a class='no-print' href=\"javascript:saveSvgFromParentDiv('svgWrapper1','Proteins filtered.svg');\" >Save figure</a></div>")
invisible(dev.off())

```

<br>

```{r}
# Curves
cytoc_ref = cytoc_ref[order(as.Date(cytoc_ref$AcquiredTime)),]
centered_rt_median_ref = c()
for (date in unique(cytoc_ref$AcquiredTime)){
  sub = subset(cytoc_ref, cytoc_ref$AcquiredTime==date)
  median = median(sub$centered_rt)
  centered_rt_median_ref = c(centered_rt_median_ref,median)
}

whiskers = boxplot.stats(centered_rt_median_ref)$stats[c(1, 5)]
sd = sd(centered_rt_median_ref)

cytoc_test = cytoc_test[order(as.Date(cytoc_test$AcquiredTime)),]
centered_rt_median_test = c()
for (date in unique(cytoc_test$AcquiredTime)){
  sub = subset(cytoc_test, cytoc_test$AcquiredTime==date)
  median = median(sub$centered_rt)
  centered_rt_median_test = c(centered_rt_median_test,median)
}

gg3 = ggplot() +
  geom_ribbon(aes(x=unique(cytoc_test$AcquiredTime),ymin=centered_rt_median_test-2*sd,ymax=centered_rt_median_test+2*sd,group=1,fill="SD"),alpha=0.2) +
  geom_line(aes(x= unique(cytoc_test$AcquiredTime),y=centered_rt_median_test,group=1, colour="Median RT"),size=0.8)+
  geom_hline(aes(yintercept=whiskers[1],linetype = "Acceptable range"),colour=colour[1],size=1)+
  geom_hline(yintercept=whiskers[2],linetype = "dashed",col=colour[1],size=1)+
  scale_colour_manual("Query",values=c("Median RT"=colour[2])) +
  scale_fill_manual("",values=c("SD"=colour[2])) +
   scale_linetype_manual("Reference", values = c(2, 2), 
                      guide = guide_legend(override.aes = list(color = colour[1]))) +
  ggtitle("RT distributions validity across acquired times")+
  xlab("Acquired time")+
  ylab("Centered RT")+
 theme(axis.text.x=element_text(angle=90,size=30),
       axis.text.y=element_text(size=30),
       plot.title=element_text(size=34),
       legend.text=element_text(size=30),
       legend.title = element_text(size=30),
       axis.title=element_text(size=30))

s <- svgstring(width=20,height=10)
plot(gg3)
htmltools::HTML("<div id=\"svgWrapper1\" ",s(),"<a class='no-print' href=\"javascript:saveSvgFromParentDiv('svgWrapper1','Proteins filtered.svg');\" >Save figure</a></div>")
invisible(dev.off())
```

<br>

```{r fig.caption="Z-score = (RT_obs - median_ref)/sd"}

#df z-score for ploting
df_z_rt = NULL
for (date in unique(cytoc_test$AcquiredTime)){
  sub = subset(cytoc_test,cytoc_test$AcquiredTime==date)
  #RT
  median = median(sub$z_rt)
  min = min(sub$z_rt)
  max = max(sub$z_rt)
  df_z_rt = rbind(df_z_rt,c(date,median,min,max))
}
colnames(df_z_rt) = c("AcquiredTime","median","min","max")
data_z = data.frame(df_z_rt)

gg4 = ggplot(data_z) +
  geom_ribbon(aes(x=AcquiredTime,ymin=as.numeric(as.character(min)),ymax=as.numeric(as.character(max)),group=1,fill="Range Z-score"),alpha=0.2) +
  geom_line(aes(x=AcquiredTime,y=as.numeric(as.character(median)) ,group=1, colour="Median Z-score"),size=0.8)+
  scale_colour_manual("",values=c("Median Z-score"=colour[2])) +
  scale_fill_manual("",values=c("Range Z-score"=colour[2])) +
  ggtitle("RT Z-score deviation")+
  xlab("Acquired time")+
  ylab("Z-score")+
 theme(axis.text.x=element_text(angle=90,size=18),
       axis.text.y=element_text(size=20),
       plot.title=element_text(size=28),
       legend.text=element_text(size=18),
       legend.title = element_text(size=18),
       axis.title=element_text(size=18))

plot(gg4)

```
Z-score = (RT_obs - median_ref)/sd

<br>
<br>

## Intensity
<br>

```{r intensities, fig.cap="log2(intensity/median)"}

gg2 = ggplot(data = data, aes(x = Precursor, y = log2(centered_intensity))) + 
  geom_boxplot(aes(col = Source),size=0.8)+
  ggtitle("Intensity distribution accross peptides")+
  ylab("Centered intensities")+
  theme(axis.text.x = element_text(angle=90,size=18),
        axis.text.y=element_text(size=20),
        plot.title=element_text(size=28),
        legend.text=element_text(size=18),
        legend.title = element_text(size=18),
        axis.title=element_text(size=18))

# Histogram
gg1 = ggplot() + 
  geom_histogram(data=cytoc_test, aes(x=log2(centered_intensity)),fill=colour[2],col=colour[2],alpha = 0.4)+
  geom_histogram(data=cytoc_ref, aes(x=log2(centered_intensity)),fill=colour[1],col=colour[1],alpha = 0.4)+
  ggtitle("Intensity distribution accross series")+
  xlab("Centered intensities")+
  theme(axis.text.x = element_text(angle=90,size=18),
        axis.text.y=element_text(size=20),
        plot.title=element_text(size=28),
        legend.text=element_text(size=18),
        legend.title = element_text(size=18),
        axis.title=element_text(size=18))

grid.arrange(arrangeGrob(gg1+theme(plot.margin = unit(c(0,2,0,0), "cm"))), 
                arrangeGrob(gg2),
                ncol=2,nrow=1)

```

<br>

```{r}
# Curves
cytoc_ref = cytoc_ref[order(as.Date(cytoc_ref$AcquiredTime)),]
centered_intensity_median_ref = c()
for (date in unique(cytoc_ref$AcquiredTime)){
  sub = subset(cytoc_ref, cytoc_ref$AcquiredTime==date)
  median = median(sub$centered_intensity)
  centered_intensity_median_ref = c(centered_intensity_median_ref,median)
}

whiskers = boxplot.stats(centered_intensity_median_ref)$stats[c(1, 5)]
sd = sd(centered_intensity_median_ref)

cytoc_test = cytoc_test[order(as.Date(cytoc_test$AcquiredTime)),]
centered_intensity_median_test = c()
for (date in unique(cytoc_test$AcquiredTime)){
  sub = subset(cytoc_test, cytoc_test$AcquiredTime==date)
  median = median(sub$centered_intensity)
  centered_intensity_median_test = c(centered_intensity_median_test,median)
}

gg3 = ggplot() +
  geom_ribbon(aes(x=unique(cytoc_test$AcquiredTime),ymin=centered_intensity_median_test-2*sd,ymax=centered_intensity_median_test+2*sd,group=1,fill="SD"),alpha=0.2) +
  geom_line(aes(x= unique(cytoc_test$AcquiredTime),y=centered_intensity_median_test,group=1, colour="Median intensity"),size=0.8)+
  geom_hline(aes(yintercept=whiskers[1],linetype = "Acceptable median range"),colour=colour[1],size=1)+
  geom_hline(yintercept=whiskers[2],linetype = "dashed",col=colour[1],size=1)+
  scale_colour_manual("Query",values=c("Median intensity"=colour[2])) +
  scale_fill_manual("",values=c("SD"=colour[2])) +
   scale_linetype_manual("Reference", values = c(2, 2), 
                      guide = guide_legend(override.aes = list(color = colour[1]))) +
  ggtitle("Median intensity deviation")+
  xlab("Acquired time")+
  ylab("Centered intensities")+
 theme(axis.text.x=element_text(angle=90,size=18),
       axis.text.y=element_text(size=20),
       plot.title=element_text(size=28),
       legend.text=element_text(size=18),
       legend.title = element_text(size=18),
       axis.title=element_text(size=18))

plot(gg3)
```

<br>

```{r fig.cap="log2(intensity/median)"}

#df FC for ploting
df_fc = NULL
for (date in unique(cytoc_test$AcquiredTime)){
  sub = subset(cytoc_test,cytoc_test$AcquiredTime==date)
  median = median(sub$FC)
  min = min(sub$FC)
  max = max(sub$FC)
  df_fc = rbind(df_fc,c(date,median,min,max))
}
colnames(df_fc) = c("AcquiredTime","median","min","max")
df_fc = data.frame(df_fc)

gg4 = ggplot(df_fc) +
  geom_ribbon(aes(x=AcquiredTime,ymin=as.numeric(as.character(min)),ymax=as.numeric(as.character(max)),group=1,fill="Range FC"),alpha=0.2) +
  geom_line(aes(x=AcquiredTime,y=as.numeric(as.character(median)) ,group=1, colour="Median FC"),size=0.8)+
  scale_colour_manual("",values=c("Median FC"=colour[2])) +
  scale_fill_manual("",values=c("Range FC"=colour[2])) +
  ggtitle("Intensity FC deviation")+
  xlab("Acquired time")+
  ylab("log2(FC)")+
 theme(axis.text.x=element_text(angle=90,size=18),
       axis.text.y=element_text(size=20),
       plot.title=element_text(size=28),
       legend.text=element_text(size=18),
       legend.title = element_text(size=18),
       axis.title=element_text(size=18))

plot(gg4)

```

<br>
<br>

## PPM

```{r ppm}

gg2 = ggplot(data = data, aes(x = Precursor, y = PPM)) + 
  geom_boxplot(aes(col = Source),size=0.8)+
  ggtitle("PPM distribution accross peptides")+
  ylab("Centered PPM")+
  theme(axis.text.x = element_text(angle=90,size=18),
        axis.text.y=element_text(size=20),
        plot.title=element_text(size=28),
        legend.text=element_text(size=18),
        legend.title = element_text(size=18),
        axis.title=element_text(size=18))

# Histogram
gg1 = ggplot() + 
  geom_histogram(data=cytoc_test, aes(x=PPM),fill=colour[2],col=colour[2],alpha = 0.4)+
  geom_histogram(data=cytoc_ref, aes(x=PPM),fill=colour[1],col=colour[1],alpha = 0.4)+
  ggtitle("PPM distribution accross series")+
  xlab("PP")+
  theme(axis.text.x = element_text(angle=90,size=18),
        axis.text.y=element_text(size=20),
        plot.title=element_text(size=28),
        legend.text=element_text(size=18),
        legend.title = element_text(size=18),
        axis.title=element_text(size=18))

grid.arrange(arrangeGrob(gg1+theme(plot.margin = unit(c(0,2,0,0), "cm"))), 
                arrangeGrob(gg2),
                ncol=2,nrow=1)

```

<br>

```{r}
# Curves
cytoc_ref = cytoc_ref[order(as.Date(cytoc_ref$AcquiredTime)),]
ppm_median_ref = c()
for (date in unique(cytoc_ref$AcquiredTime)){
  sub = subset(cytoc_ref, cytoc_ref$AcquiredTime==date)
  median = median(sub$PPM)
  ppm_median_ref = c(ppm_median_ref,median)
}

whiskers = boxplot.stats(ppm_median_ref)$stats[c(1, 5)]
sd = sd(ppm_median_ref)

cytoc_test = cytoc_test[order(as.Date(cytoc_test$AcquiredTime)),]
ppm_median_test = c()
ppm_sd_test = c()
for (date in unique(cytoc_test$AcquiredTime)){
  sub = subset(cytoc_test, cytoc_test$AcquiredTime==date)
  median = median(sub$PPM)
  ppm_median_test = c(ppm_median_test,median)
  sd = sd(sub$PPM)
  ppm_sd_test = c(ppm_sd_test,sd)
}

gg3 = ggplot() +
  geom_ribbon(aes(x=unique(cytoc_test$AcquiredTime),ymin=ppm_median_test-2*ppm_sd_test,ymax=ppm_median_test+2*ppm_sd_test,group=1,fill="SD"),alpha=0.2) +
  geom_line(aes(x= unique(cytoc_test$AcquiredTime),y=ppm_median_test,group=1, colour="Median ppm"),size=0.8)+
  geom_hline(aes(yintercept=whiskers[1],linetype = "Threshold"),colour=colour[1],size=1)+
  #geom_hline(yintercept=whiskers[2],linetype = "dashed",col=colour[1],size=1)+
  scale_colour_manual("Query",values=c("Median ppm"=colour[2])) +
  scale_fill_manual("",values=c("SD"=colour[2])) +
   scale_linetype_manual("Reference", values = c(2, 2), 
                      guide = guide_legend(override.aes = list(color = colour[1]))) +
  ggtitle("Median ppm deviation")+
  xlab("Acquired time")+
  ylab("ppm")+
 theme(axis.text.x=element_text(angle=90,size=18),
       axis.text.y=element_text(size=20),
       plot.title=element_text(size=28),
       legend.text=element_text(size=18),
       legend.title = element_text(size=18),
       axis.title=element_text(size=18))

plot(gg3)
```



<br>

<div id="banner">
# Acquired times validity
</div>
<br>

## Global visualization
<br>

```{r}
whiskers = boxplot.stats(cytoc_ref$centered_rt)$stats[c(1, 5)]
min_rt = whiskers[1]
max_rt = whiskers[2]
whiskers = boxplot.stats(log2(cytoc_ref$centered_intensity))$stats[c(1, 5)]
min_intensity = 0.3*median(cytoc_ref$centered_intensity)
max_intensity = NA
whiskers = boxplot.stats(cytoc_ref$PPM)$stats[c(1, 5)]
min_ppm = NA
max_ppm = 10

```

```{r message=FALSE}

rt_test = c()
intensity_test=c()
ppm_test = c()

for (date in unique(cytoc_test$AcquiredTime)){
  
  sub = subset(cytoc_test,cytoc_test$AcquiredTime==date)
  
  if(T%in%(sub$centered_rt<min_rt) || T%in%(sub$centered_rt>max_rt)){
    rt = F
  }else{
    rt = T
  }
  if(T%in%(sub$centered_intensity<min_intensity)){
    intensity = F
  }else{
    intensity = T
  }
  if(T%in%(sub$PPM>max_ppm)){
    ppm = F
  }else{
    ppm = T
  }
  
  rt_test = c(rt_test,rt)
  intensity_test = c(intensity_test,intensity)
  ppm_test = c(ppm_test,ppm)
}

heatmapDF = data.frame(unique(cytoc_test$AcquiredTime),rt_test,intensity_test,ppm_test)
colnames(heatmapDF)=c("AcquiredTime","RT","Intensity","PPM")
heatmapDF_plot = melt(heatmapDF,id.vars = "AcquiredTime")

gg = ggplot(data = heatmapDF_plot, aes(x = variable, y = ordered(AcquiredTime, levels=rev(levels(AcquiredTime))))) + 
  geom_tile(aes(fill = value), color = "white", size = 1,alpha=0.5) +
  scale_fill_manual("",breaks=c(F,T),values=c(colour[1],colour[2]))+
  xlab("Metrics") + 
  ggtitle("Metrics validity assessment") + 
  theme(axis.text.x = element_text(size=22),
        axis.text.y=element_text(size=22),
        plot.title=element_text(size=28),
        legend.text=element_text(size=24),
        legend.title = element_text(size=24),
        axis.title=element_text(size=18))

s <- svgstring(width=20,height=10)
if(!(F%in%heatmapDF_plot$value)){
    plot(gg+ scale_fill_manual("",values=c(colour[2]),breaks=c(T),drop = FALSE))
  }else{
    if(!(T%in%heatmapDF_plot$value)){
    plot(gg+ scale_fill_manual("",values=c(colour[1]),breaks=c(F),drop = FALSE))
    }else{
      plot(gg)
    }
  }
htmltools::HTML("<div id=\"svgWrapper1\" ",s(),"<a class='no-print' href=\"javascript:saveSvgFromParentDiv('svgWrapper1','Proteins filtered.svg');\" >Save figure</a></div>")
invisible(dev.off())


```

<br>

<div class="row">
<div class = "col-md-4">
```{r comment=NA, opts.label="kill_prefix",results='asis'}
valid = subset(heatmapDF,heatmapDF$Intensity==T & heatmapDF$RT==T & heatmapDF$PPM==T)$AcquiredTime
kable(valid,format="html",col.names = NULL,caption = "Valid acquired times") %>% kable_styling(full_width = T,position = "left")

```
<br>
</div>
<div class = "col-md-4">
```{r comment=NA, opts.label="kill_prefix",results='asis'}
invalid = subset(heatmapDF,heatmapDF$Intensity==F | heatmapDF$RT==F | heatmapDF$PPM==F)$AcquiredTime

kable(invalid,format="html",col.names = NULL,caption = "Invalid acquired times") %>% kable_styling(full_width = T,position = "left")
#cat(paste('-', invalid), sep = '\n') 
```
<br>
</div>
<div class = "col-md-4">
```{r results='asis'}
bounds = matrix(c(min_rt,max_rt,2^min_intensity,max_intensity,min_ppm,max_ppm),nrow=2)
bounds = data.frame(bounds)
colnames(bounds)=c("Centered RT","Centered intensity","Centered PPM")
rownames(bounds)=c("min","max")

kable(bounds,format="html",caption = "Boudaries") %>% kable_styling(full_width = F,position = "left")
```
</div>
</div>

```{r opts.label="kill_prefix", results='asis'}
# 
# plots = c()
# 
# for (date in unique(cytoc_test$AcquiredTime)){
#   sub = subset(cytoc_test, cytoc_test$AcquiredTime==date)
#   
#   #cat(text_spec(date, bold=T, font_size=18 ))
#   
#   heatmapDF = NULL
# 
#   for (peptide in unique(cytoc_test$Precursor)){
#   
#     sub2 = subset(sub,sub$Precursor==peptide)
#   
#     if(T%in%(sub2$centered_rt<min_rt) || T%in%(sub$centered_rt>max_rt)){
#       rt = F
#     }else{
#       rt = T
#     }
#     if(T%in%(log2(sub2$centered_intensity)<min_intensity) || T%in%(log2(sub2$centered_intensity)>max_intensity)){
#       intensity = F
#    }else{
#       intensity = T
#     }
#    if(T%in%(sub2$PPM<min_ppm) || T%in%(sub2$PPM>max_ppm)){
#       ppm = F
#    }else{
#      ppm = T
#    }
#   
#   row = c(peptide,rt,intensity,ppm)
#   heatmapDF = rbind(heatmapDF,row)
#   }
#   
#   heatmapDF = data.frame(heatmapDF)
#   colnames(heatmapDF)=c("Precursor","RT","Intensity","PPM")
#   heatmapDF_plot = melt(heatmapDF,id.vars = "Precursor")
#   
#   gg = ggplot(data = heatmapDF_plot, aes(x = variable, y = Precursor)) + 
#   geom_tile(aes(fill = value), color = "white", size = 1,alpha=0.5) +
#   scale_fill_manual("",values=c(colour[1],colour[2]),breaks=c(F,T),drop = FALSE)+
#   xlab("Metrics") + 
#   ggtitle("Metrics validity assessment for each precursor") + 
#   theme(axis.text.x = element_text(size=15),
#         axis.text.y=element_text(size=20),
#         plot.title=element_text(size=28),
#         legend.text=element_text(size=13),
#         legend.title = element_text(size=16),
#         axis.title=element_text(size=16))
#   
#   # if(!(F%in%heatmapDF_plot$value)){
#   #  gg+ scale_fill_manual("",values=c(colour[2]),breaks=c(T),drop = FALSE)
#   # }else{
#   #   if(!(T%in%heatmapDF_plot$value)){
#   #   gg+ scale_fill_manual("",values=c(colour[1]),breaks=c(F),drop = FALSE)
#   #   }else{
#   #     plot(gg)
#   #   }
#   # }
#   
#   plots = c(plots,gg)
#   if (length(plots)==27){
#     grid.arrange(arrangeGrob(plots[1:9]), 
#                 arrangeGrob(plots[9:18]), 
#                 arrangeGrob(plots[18:27]), 
#                 ncol=3,nrow=1)
#     plots = c()
#   }
# }



```

<div id="banner">
# Precursor validity
</div>
<br>

```{r results='asis'}

for (precursor in unique(cytoc_test$Precursor)){
  sub = subset(cytoc_test, cytoc_test$Precursor==precursor)
  
  cat(text_spec(precursor, bold=T, font_size=18, color="#3686D5"))
  
  whiskers = boxplot.stats(sub$Best.RT)$stats[c(1, 5)]
  min_rt = whiskers[1]
  max_rt = whiskers[2]
  whiskers = boxplot.stats(log10(cytoc_ref$TotalArea))$stats[c(1, 5)]
  min_intensity = whiskers[1]
  max_intensity = whiskers[2]
  whiskers = boxplot.stats(cytoc_ref$PPM)$stats[c(1, 5)]
  min_ppm = whiskers[1]
  max_ppm = whiskers[2]
  # 
  # heatmapDF = NULL
  # 
  # for (date in unique(cytoc_test$AcquiredTime)){
  # 
  #   sub2 = subset(sub,sub$AcquiredTime==date)
  # 
  #   if(T%in%(sub2$centered_rt<min_rt) || T%in%(sub$centered_rt>max_rt)){
  #     rt = F
  #   }else{
  #     rt = T
  #   }
  #   if(T%in%(log2(sub2$centered_intensity)<min_intensity) || T%in%(log2(sub2$centered_intensity)>max_intensity)){
  #     intensity = F
  #  }else{
  #     intensity = T
  #   }
  #  if(T%in%(sub2$PPM<min_ppm) || T%in%(sub2$PPM>max_ppm)){
  #     ppm = F
  #  }else{
  #    ppm = T
  #  }
  # 
  # row = c(date,rt,intensity,ppm)
  # heatmapDF = rbind(heatmapDF,row)
  # }
  # 
  # heatmapDF = data.frame(heatmapDF)
  # colnames(heatmapDF)=c("AcquiredTime","RT","Intensity","PPM")
  # heatmapDF_plot = melt(heatmapDF,id.vars = "AcquiredTime")
  # 
  # gg1 = ggplot(data = heatmapDF_plot, aes(x = variable, y = AcquiredTime)) + 
  # geom_tile(aes(fill = value), color = "white", size = 1,alpha=0.5) +
  # scale_fill_manual("",values=c(colour[1],colour[2]),breaks=c(F,T),drop = FALSE)+
  # xlab("AcquiredTime") + 
  # ggtitle("") + 
  # theme(axis.text.x = element_text(size=15),
  #       axis.text.y=element_text(size=20),
  #       plot.title=element_text(size=28),
  #       legend.text=element_text(size=13),
  #       legend.title = element_text(size=16),
  #       axis.title=element_text(size=16))
  # 
  # if(!(F%in%heatmapDF_plot$value)){
  #  gg1+ scale_fill_manual("",values=c(colour[2]),breaks=c(T),drop = FALSE)
  # }else{
  #   if(!(T%in%heatmapDF_plot$value)){
  #   gg1+ scale_fill_manual("",values=c(colour[1]),breaks=c(F),drop = FALSE)
  #   }else{
  #     plot(gg1)
  #   }
  # }
  
  gg1 = ggplot(data = sub) +
    geom_line(aes(x = AcquiredTime, y = Best.RT,group=1,col="RT in test serie"),show.legend = F,size=0.8)+
    geom_hline(aes(yintercept=min_rt, color="Acceptable range"),linetype="dashed",size=1) +
    geom_hline(yintercept=max_rt, color=colour[1],linetype="dashed",size=1) +
    scale_color_manual("",values=c("RT in test serie"=colour[2],"Acceptable range"=colour[1])) +
    ggtitle(paste0("RT deviation of ",precursor))+
    ylab("RT")+
     theme(axis.text.x=element_text(angle=90,size=15),
         axis.text.y=element_text(size=20),
         plot.title=element_text(size=28),
         legend.text=element_text(size=18),
         legend.title = element_text(size=18),
         axis.title=element_text(size=18),
         plot.margin = unit(c(2,0,2,0), "cm"))
  
  plot(gg1)
  
  gg2 = ggplot(data = sub) +
    geom_line(aes(x = AcquiredTime, y = log10(TotalArea),group=1,col="Intensities in test serie"),show.legend = F,size=0.8)+
    geom_hline(aes(yintercept=min_intensity, color="Acceptable range"),linetype="dashed",size=1) +
    geom_hline(yintercept=max_intensity, color=colour[1],linetype="dashed",size=1) +
    scale_color_manual("",values=c("Intensities in test serie"=colour[2],"Acceptable range"=colour[1])) +
    ggtitle(paste0("Intensity deviation of ",precursor))+
    ylab("log(intensity)")+
     theme(axis.text.x=element_text(angle=90,size=18),
         axis.text.y=element_text(size=20),
         plot.title=element_text(size=28),
         legend.text=element_text(size=18),
         legend.title = element_text(size=18),
         axis.title=element_text(size=18),
         plot.margin = unit(c(0,0,2,0),"cm"))
  
  plot(gg2)
  
  gg1 = ggplot(data = sub) +
    geom_line(aes(x = AcquiredTime, y = PPM,group=1,col="PPM in test serie"),show.legend = F,size=0.8)+
    geom_hline(aes(yintercept=min_ppm, color="Acceptable range"),linetype="dashed",size=1) +
    geom_hline(yintercept=max_ppm, color=colour[1],linetype="dashed",size=1) +
    scale_color_manual("",values=c("PPM in test serie"=colour[2],"Acceptable range"=colour[1])) +
    ggtitle(paste0("PPM deviation of ",precursor))+
    ylab("PPM")+
     theme(axis.text.x=element_text(angle=90,size=18),
         axis.text.y=element_text(size=20),
         plot.title=element_text(size=28),
         legend.text=element_text(size=18),
         legend.title = element_text(size=18),
         axis.title=element_text(size=18),
         plot.margin = unit(c(0,0,2,0),"cm"))
  
  plot(gg1)
  
}
```

<!-- ```{r opts.label="kill_prefix", results='asis'} -->

<!-- colour = unique(ggplot_build(gg1)$data[[1]]$colour) -->
<!-- input$Precursors = paste0(input$Precursor," (",input$mz,")") -->

<!-- i=1 -->

<!-- for (peptide in unique(input$Precursors)){ -->
<!--   sub = subset(input, input$Precursors==peptide) -->
<!--   peptide_name = unique(sub$Precursor) -->

<!-- gg1 =   ggplot(data = sub) + -->
<!--   geom_line(aes(x = AcquiredTime, y = TotalArea,group=1),col=colour[i],show.legend = F,size=0.8)+ -->
<!--   ggtitle(paste0("Absolute intensity deviation of ",peptide_name))+ -->
<!--   ylab("Intensity")+ -->
<!--    theme(axis.text.x=element_text(angle=90,size=15), -->
<!--          axis.text.y=element_text(size=20), -->
<!--          plot.title=element_text(size=28), -->
<!--          legend.text=element_text(size=13), -->
<!--          legend.title = element_text(size=16), -->
<!--          axis.title=element_text(size=16)) -->

<!-- gg2 =   ggplot(data = sub) + -->
<!--   geom_line(aes(x = AcquiredTime, y = Best.RT,group=1),col=colour[i],show.legend = F,size=0.8)+ -->
<!--   ggtitle(paste0("Absolute RT deviation of ",peptide_name))+ -->
<!--   ylab("RT")+ -->
<!--   theme(axis.text.x=element_text(angle=90,size=15), -->
<!--         axis.text.y=element_text(size=20), -->
<!--         plot.title=element_text(size=28), -->
<!--         legend.text=element_text(size=13), -->
<!--         legend.title = element_text(size=16), -->
<!--         axis.title=element_text(size=16)) -->

<!-- gg3 =  ggplot(data = sub) + -->
<!--   geom_line(aes(x = AcquiredTime, y = sub$PPM,group=1),col=colour[i],show.legend = F,size=0.8)+ -->
<!--   ggtitle(paste0("Absolute PPM deviation of ",peptide_name))+ -->
<!--   ylab("PPM")+ -->
<!--   theme(axis.text.x=element_text(angle=90,size=15), -->
<!--         axis.text.y=element_text(size=20), -->
<!--         plot.title=element_text(size=28), -->
<!--         legend.text=element_text(size=13), -->
<!--         legend.title = element_text(size=16), -->
<!--         axis.title=element_text(size=16)) -->

<!--   cat(text_spec(peptide, color=as.character(colour[i]), bold=T, font_size=18 )) -->

<!--   if(layout){ -->
<!--     grid.arrange(arrangeGrob(gg1+theme(plot.margin=unit(c(2,0,2,0),"cm"),axis.text.x=element_text(angle=90,size=13),plot.title=element_text(size=15))),  -->
<!--                  arrangeGrob(gg2+theme(plot.margin=unit(c(2,0,2,0),"cm"),axis.text.x=element_text(angle=90,size=13),plot.title=element_text(size=15))), -->
<!--                  arrangeGrob(gg3+theme(plot.margin=unit(c(2,0,2,0),"cm"),axis.text.x=element_text(angle=90,size=13),plot.title=element_text(size=15))), -->
<!--                  ncol=3,nrow=1) -->
<!--   }else{ -->
<!--     plot(gg1+theme(plot.margin = unit(c(2,0,2,0), "cm"))) -->
<!--     plot(gg2+theme(plot.margin = unit(c(0,0,2,0),"cm"))) -->
<!--     plot(gg3+theme(plot.margin = unit(c(0,0,2,0),"cm"))) -->
<!--   } -->

<!--   i=i+1 -->
<!-- } -->

<!-- ``` -->

