---
title: "CytoC"
output:
  html_document
params:
  file_name : "cytoc_xics_ref.csv"
---

<style type="text/css">

body{ /* Normal  */
      font-size: 12px;
  }
h1.title {
  font-size: 20px;
  color: #3686D5;
  font-weight:bold;
  text-align: center;
}
h1 { /* Header 1 */
  font-size: 28px;
  color: white;
  font-weight:bold;
}
h2 { /* Header 2 */
  font-size: 20px;
  color: #3686D5;
  font-weight:bold;
}
div#banner {
       background-color: #3686D5; 
       width: 100%; 
}
</style>

<script>
function saveSvgFromParentDiv(divElId, name) {
	var divSvgWrapperEl = document.getElementById(divElId);

	var svgEl = divSvgWrapperEl.firstElementChild;
  svgEl.setAttribute("xmlns", "http://www.w3.org/2000/svg");
  var svgData = svgEl.outerHTML;
  var preface = '<?xml version="1.0" standalone="no"?>\r\n';
  var svgBlob = new Blob([preface, svgData], {type:"image/svg+xml;charset=utf-8"});
  var svgUrl = URL.createObjectURL(svgBlob);
  var downloadLink = document.createElement("a");
  downloadLink.href = svgUrl;
  downloadLink.download = name;
  document.body.appendChild(downloadLink);
  downloadLink.click();
  document.body.removeChild(downloadLink);
}
</script>


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F,warning=F,message=F,opts.label="kill_prefix",fig.dim=c(20,10))
```

```{r include=FALSE}

library(ggplot2)
library(scales)
library(grid)
library(gridExtra)
library(knitr)
library(kableExtra)
library(svglite)

```


```{r file_import, include=F}

input = read.table(params$file_name,sep=",",header=T)

# Labels for legend (add theoretical mz to precursor id)
input$Precursors = paste0(input$Precursor,"\n (",input$mz,")")

# Order dates
input$AcquiredTime <- as.POSIXct(input$AcquiredTime, format = "%d/%m/%Y %H:%M")
input = input[order(input$AcquiredTime),] #Sort by date
input$AcquiredTime <- factor(input$AcquiredTime,ordered = T)

```

```{r list_file_names}

file_names = sub(";.*","",sub("RAW = ","",input$Annotations))
Link_AcquiredTime_FileName = data.frame(input$AcquiredTime,file_names)
colnames(Link_AcquiredTime_FileName) = c("Acquired time","File name")
kable(Link_AcquiredTime_FileName,format="html") %>% kable_styling(full_width = T,position = "left") %>% scroll_box(height = "200px")

```



<br>
<div id="banner">
# Retention time
</div>

## Raw RT

```{r plot_raw_rt, results='asis'}

gg1 = ggplot(data = input, aes(x = AcquiredTime, y = Best.RT,group=Precursors)) + 
  geom_line(aes(colour = Precursors),size=0.8)+
  ggtitle("Raw RT distribution")+
  ylab("Retention time") +
  theme(axis.text.x=element_text(angle=90,size=18),
        axis.text.y=element_text(size=22),
        plot.title=element_text(size=28),
        legend.text=element_text(size=20),
        legend.title = element_text(size=22),
        axis.title=element_text(size=22))

s <- svgstring(width=20,height=10)
plot(gg1)
htmltools::HTML("<div id=\"svgWrapper1\" ",s(),"<a class='no-print' href=\"javascript:saveSvgFromParentDiv('svgWrapper1','Raw RT distribution.svg');\" >Save figure</a></div>")
invisible(dev.off())

cat(text_spec("\n"))

gg2 = ggplot(data = input, aes(x = Precursor, y = Best.RT)) + 
  geom_boxplot(aes(col = Precursors),size=0.8)+
  ggtitle("RT distribution accross peptides")+
  ylab("Retention Time")+
  xlab("")+
  theme(axis.text.x = element_blank(),
        axis.text.y=element_text(size=22),
        plot.title=element_text(size=28),
        legend.text=element_text(size=20),
        legend.title = element_text(size=22),
        axis.title=element_text(size=22))

s <- svgstring(width=20,height=10)
plot(gg2)
htmltools::HTML("<div id=\"svgWrapper2\" ",s(),"<a class='no-print' href=\"javascript:saveSvgFromParentDiv('svgWrapper2','RT distribution accross peptides.svg');\" >Save figure</a></div>")
invisible(dev.off())

```

<br>

## Median relative RT


```{r plot_median_relative_rt, results='asis'}

# Median centering of RT
input = input[order(input$Precursor),] #Sort by precursor
centered_rt = c()
for (precursor in unique(input$Precursor)){
  sub = subset(input, input$Precursor==precursor)
  median = median(sub$Best.RT)
  centered_rt = c(centered_rt, sub$Best.RT-median)
}
input$centered_rt = centered_rt

# Median computing for each AcquiredTime
input = input[order(as.Date(input$AcquiredTime)),]
centered_rt_median = c()
for (date in unique(input$AcquiredTime)){
  sub = subset(input, input$AcquiredTime==date)
  median = median(sub$centered_rt)
  centered_rt_median = c(centered_rt_median,median)
}

legend = c("median",as.character(unique(input$Precursor)))
color = c("black",hue_pal()(9))

gg1 = ggplot() +
  geom_line(data = input, aes(x = AcquiredTime, y = centered_rt,group=as.factor(input$Precursor), colour = Precursors),size=0.8)+
  geom_line(aes(x= unique(input$AcquiredTime),y=centered_rt_median,group=1,linetype="median"),col="black",size=0.8)+
  ggtitle("Median RT deviation")+
  ylab("Centered retention time")+
 theme(axis.text.x=element_text(angle=90,size=18),
       axis.text.y=element_text(size=22),
       plot.title=element_text(size=28),
       legend.text=element_text(size=20),
       legend.title = element_text(size=22),
       axis.title=element_text(size=22))

s <- svgstring(width=20,height=10)
plot(gg1)
htmltools::HTML("<div id=\"svgWrapper3\" ",s(),"<a class='no-print' href=\"javascript:saveSvgFromParentDiv('svgWrapper3','Median RT deviation.svg');\" >Save figure</a></div>")
invisible(dev.off())

cat(text_spec("\n"))

gg2 = ggplot() +
  geom_boxplot(data = input,aes(x = Precursor, y = centered_rt, col = Precursors),size=0.8)+
  geom_boxplot(aes(x="1",y=centered_rt_median,linetype="median"),size=0.8)+
  ggtitle("RT distribution accross peptides")+
  ylab("RT")+
  xlab("")+
  theme(axis.text.x = element_blank(),
        axis.text.y=element_text(size=22),
        plot.title=element_text(size=28),
        legend.text=element_text(size=20),
        legend.title = element_text(size=22),
        axis.title=element_text(size=22))

s <- svgstring(width=20,height=10)
plot(gg2)
htmltools::HTML("<div id=\"svgWrapper4\" ",s(),"<a class='no-print' href=\"javascript:saveSvgFromParentDiv('svgWrapper4','RT distribution accross peptides.svg');\" >Save figure</a></div>")
invisible(dev.off())

```

_RT were normalized by computing the difference beetween each acquired RT and the median of all for each precursor._

<br>

## First time relative RT


```{r 1rst_acquiredTime_relative_RT, results='asis'}

# Centering of RT
input = input[order(input$Precursor),] #Sort by precursor

## Find the reference
nb_precursors = length(unique(input$Precursor))
ref_found = F
i=1
while(ref_found==F){
  ref_data = subset(input,input$AcquiredTime==factor(input$AcquiredTime)[i])
  nb_precursors_test = length(unique(ref_data$Precursor))
  if(nb_precursors_test==nb_precursors){
    ref_found=T
  }else{
    i=i+1
  }
}

## Compute FC
if(ref_found){
  
  centered_rt = c()
  for (precursor in unique(input$Precursor)){
    sub = subset(input, input$Precursor==precursor)
    ref = subset(ref_data,ref_data$Precursor==precursor)$Best.RT
    centered_rt = c(centered_rt, sub$Best.RT-ref)
  }
  input$centered_rt = centered_rt
  
  # Median computing for each AcquiredTime
  input = input[order(as.Date(input$AcquiredTime)),]
  centered_rt_median = c()
  for (date in unique(input$AcquiredTime)){
    sub = subset(input, input$AcquiredTime==date)
    median = median(sub$centered_rt)
    centered_rt_median = c(centered_rt_median,median)
  }

  legend = c("median",as.character(unique(input$Precursor)))
  color = c("black",hue_pal()(9))

  gg1 = ggplot() +
    geom_line(data = input, aes(x = AcquiredTime, y = centered_rt,group=as.factor(input$Precursor), colour = Precursors),size=0.8)+
    geom_line(aes(x= unique(input$AcquiredTime),y=centered_rt_median,group=1,linetype="median"),col="black",size=0.8)+
    ggtitle("RT deviation related to 1rst acquired time")+
    ylab("Centered retention time")+
    theme(axis.text.x=element_text(angle=90,size=18),
       axis.text.y=element_text(size=22),
       plot.title=element_text(size=28),
       legend.text=element_text(size=20),
       legend.title = element_text(size=22),
       axis.title=element_text(size=22))
  
  s <- svgstring(width=20,height=10)
  plot(gg1)
  cat(htmltools::HTML("<div id=\"svgWrapper5\" ",s(),"<a class='no-print' href=\"javascript:saveSvgFromParentDiv('svgWrapper5','RT deviation related to 1rst acquired time.svg');\" >Save figure</a></div>"))
  invisible(dev.off())
  
  cat(text_spec("\n"))

  gg2 = ggplot() +
    geom_boxplot(data = input,aes(x = Precursor, y = centered_rt, col = Precursors),size=0.8)+
    geom_boxplot(aes(x="1",y=centered_rt_median,linetype="median"),size=0.8)+
    ggtitle("RT distribution accross peptides")+
    ylab("RT")+
    xlab("")+
    theme(axis.text.x = element_blank(),
        axis.text.y=element_text(size=22),
        plot.title=element_text(size=28),
        legend.text=element_text(size=20),
        legend.title = element_text(size=22),
        axis.title=element_text(size=22))

  s <- svgstring(width=20,height=10)
  plot(gg2)
  cat(htmltools::HTML("<div id=\"svgWrapper6\" ",s(),"<a class='no-print' href=\"javascript:saveSvgFromParentDiv('svgWrapper6','RT distribution accross peptides.svg');\" >Save figure</a></div>"))
  invisible(dev.off())
  
  cat(text_spec(paste0("RT were normalized by computing the difference beetween each acquired RT and the first acquired time where all precursors were observed (",ref_data$AcquiredTime[1],")"), italic=T, font_size="12px"))
  
}else{
  cat(text_spec("No acquired time at which one all precursors were observed was found."))
}

```


<br>
<div id="banner">
# Intensity
</div>

<br>

## Raw intensities


```{r plot_raw_intensities, results='asis'}

gg1 = ggplot(data = input, aes(x = AcquiredTime, y = TotalArea,group=as.factor(input$Precursor))) +
  geom_line(aes(colour = Precursors),size=0.8)+
  ggtitle("Raw intensity distribution")+
  ylab("Intensity")+
  theme(axis.text.x=element_text(angle=90,size=18),
        axis.text.y=element_text(size=22),
        plot.title=element_text(size=28),
        legend.text=element_text(size=20),
        legend.title = element_text(size=22),
        axis.title=element_text(size=22))

s <- svgstring(width=20,height=10)
plot(gg1)
htmltools::HTML("<div id=\"svgWrapper7\" ",s(),"<a class='no-print' href=\"javascript:saveSvgFromParentDiv('svgWrapper7','Raw intensity distribution.svg');\" >Save figure</a></div>")
invisible(dev.off())

cat(text_spec("\n"))

gg2 = ggplot(data = input, aes(x = Precursor, y = TotalArea)) +
  geom_boxplot(aes(col = Precursors),size=0.8)+
  ggtitle("Intensity distribution accross peptides")+
  ylab("intensity")+
  xlab("")+
  theme(axis.text.x = element_blank(),
        axis.text.y=element_text(size=22),
        plot.title=element_text(size=28),
        legend.text=element_text(size=20),
        legend.title = element_text(size=22),
        axis.title=element_text(size=22))

s <- svgstring(width=20,height=10)
plot(gg2)
htmltools::HTML("<div id=\"svgWrapper8\" ",s(),"<a class='no-print' href=\"javascript:saveSvgFromParentDiv('svgWrapper8','Intensity distribution accross peptides.svg');\" >Save figure</a></div>")
invisible(dev.off())

```

<br>

## Log intensities

```{r plot_log_intensities, results='asis'}

gg1 = ggplot(data = input, aes(x = AcquiredTime, y = log10(TotalArea),group=as.factor(input$Precursor)),size=0.8) +
  geom_line(aes(colour = Precursors),size=0.8)+
  ggtitle("Log intensity deviation")+
  ylab("log(intensity)")+
  theme(axis.text.x=element_text(angle=90,size=18),
        axis.text.y=element_text(size=22),
        plot.title=element_text(size=28),
        legend.text=element_text(size=20),
        legend.title = element_text(size=22),
        axis.title=element_text(size=22))

s <- svgstring(width=20,height=10)
plot(gg1)
htmltools::HTML("<div id=\"svgWrapper9\" ",s(),"<a class='no-print' href=\"javascript:saveSvgFromParentDiv('svgWrapper9','Log intensity deviation.svg');\" >Save figure</a></div>")
invisible(dev.off())

cat(text_spec("\n"))

gg2 = ggplot(data = input, aes(x = Precursor, y = log10(TotalArea)),size=0.8) +
  geom_boxplot(aes(col = Precursors),size=0.8)+
  ggtitle("Log intensity distribution accross peptides")+
  ylab("log(intensity)")+
  xlab("")+
  theme(axis.text.x = element_blank(),
        axis.text.y=element_text(size=22),
        plot.title=element_text(size=28),
        legend.text=element_text(size=20),
        legend.title = element_text(size=22),
        axis.title=element_text(size=22))

s <- svgstring(width=20,height=10)
plot(gg2)
htmltools::HTML("<div id=\"svgWrapper10\" ",s(),"<a class='no-print' href=\"javascript:saveSvgFromParentDiv('svgWrapper10','Log intensity distribution accross peptides.svg');\" >Save figure</a></div>")
invisible(dev.off())

```

<br>

## Median relative intensities


```{r median_centering_intensities, results='asis'}

# Median centering
input = input[order(input$Precursor),] # Sort by precursor
centered_intensity = c()
for (precursor in unique(input$Precursor)){
  sub = subset(input, input$Precursor==precursor)
  median = median(sub$TotalArea)
  centered_intensity = c(centered_intensity, sub$TotalArea/median)
}
input$centered_intensity = centered_intensity

# Median computing for each AcquiredTime
input = input[order(as.Date(input$AcquiredTime)),]
centered_intensity_median = c()
for (date in unique(input$AcquiredTime)){
  sub = subset(input, input$AcquiredTime==date)
  median = median(sub$centered_intensity)
  centered_intensity_median = c(centered_intensity_median,median)
}

gg1 = ggplot() +
  geom_line(data = input, aes(x = AcquiredTime, y = log2(centered_intensity),group=as.factor(input$Precursor),colour = Precursors),size=0.8)+
  geom_line(aes(x= unique(input$AcquiredTime),y=log2(centered_intensity_median),group=1,linetype="median"),col="black",size=0.8)+
  ggtitle("Median intensity deviation")+
  ylab("Centered intensities")+
  theme(axis.text.x=element_text(angle=90,size=18),
        axis.text.y=element_text(size=22),
        plot.title=element_text(size=28),
        legend.text=element_text(size=20),
        legend.title = element_text(size=22),
        axis.title=element_text(size=22))

s <- svgstring(width=20,height=10)
plot(gg1)
htmltools::HTML("<div id=\"svgWrapper11\" ",s(),"<a class='no-print' href=\"javascript:saveSvgFromParentDiv('svgWrapper11','Median intensity deviation.svg');\" >Save figure</a></div>")
invisible(dev.off())

cat(text_spec("\n"))

gg2 = ggplot() +
  geom_boxplot(data = input, aes(x = Precursor, y = log2(centered_intensity), col = Precursors),size=0.8)+
  geom_boxplot(aes(x="1",y=log2(centered_intensity_median),linetype="median"),size=0.8)+
  ggtitle("Intensity distribution accross peptides")+
  ylab("Centered intensities")+
  xlab("")+
  theme(axis.text.x = element_blank(),
        axis.text.y=element_text(size=22),
        plot.title=element_text(size=28),
        legend.text=element_text(size=20),
        legend.title = element_text(size=22),
        axis.title=element_text(size=22))

s <- svgstring(width=20,height=10)
plot(gg2)
htmltools::HTML("<div id=\"svgWrapper12\" ",s(),"<a class='no-print' href=\"javascript:saveSvgFromParentDiv('svgWrapper12','Intensity distribution accross peptides.svg');\" >Save figure</a></div>")
invisible(dev.off())

```

<br>

_Intensities were normalized by dividing each acquired intensity by the median of all for each precursor, and transforming the ratios by log2._

## First time relative intensities

```{r 1rst_acquiredTime_relative_intensities, results='asis'}

# Centering of intensities

## Compute FC
if(ref_found){
  
  centered_intensity = c()
  for (precursor in unique(input$Precursor)){
    sub = subset(input, input$Precursor==precursor)
    ref = subset(ref_data,ref_data$Precursor==precursor)$TotalArea
    centered_intensity = c(centered_intensity, sub$TotalArea-ref)
  }
  input$centered_intensity = centered_intensity
  
  # Median computing for each AcquiredTime
  input = input[order(as.Date(input$AcquiredTime)),]
  centered_intensity_median = c()
  for (date in unique(input$AcquiredTime)){
    sub = subset(input, input$AcquiredTime==date)
    median = median(sub$centered_intensity)
    centered_intensity_median = c(centered_intensity_median,median)
  }

  legend = c("median",as.character(unique(input$Precursor)))
  color = c("black",hue_pal()(9))

  gg1 = ggplot() +
    geom_line(data = input, aes(x = AcquiredTime, y = centered_intensity,group=as.factor(input$Precursor), colour = Precursors),size=0.8)+
    geom_line(aes(x= unique(input$AcquiredTime),y=centered_intensity_median,group=1,linetype="median"),col="black",size=0.8)+
    ggtitle("Intensity deviation related to 1rst acquired time")+
    ylab("Centered intensities")+
    theme(axis.text.x=element_text(angle=90,size=18),
       axis.text.y=element_text(size=22),
       plot.title=element_text(size=28),
       legend.text=element_text(size=20),
       legend.title = element_text(size=22),
       axis.title=element_text(size=22))
  
  s <- svgstring(width=20,height=10)
  plot(gg1)
  cat(htmltools::HTML("<div id=\"svgWrapper13\" ",s(),"<a class='no-print' href=\"javascript:saveSvgFromParentDiv('svgWrapper13','Intensity deviation related to 1rst acquired time.svg');\" >Save figure</a></div>"))
  invisible(dev.off())
  
  cat(text_spec("\n"))

  gg2 = ggplot() +
    geom_boxplot(data = input,aes(x = Precursor, y = centered_rt, col = Precursors),size=0.8)+
    geom_boxplot(aes(x="1",y=centered_rt_median,linetype="median"),size=0.8)+
    ggtitle("Intensity distribution accross peptides")+
    ylab("Intensities")+
    xlab("")+
    theme(axis.text.x = element_blank(),
        axis.text.y=element_text(size=22),
        plot.title=element_text(size=28),
        legend.text=element_text(size=20),
        legend.title = element_text(size=22),
        axis.title=element_text(size=22))

  s <- svgstring(width=20,height=10)
  plot(gg2)
  cat(htmltools::HTML("<div id=\"svgWrapper14\" ",s(),"<a class='no-print' href=\"javascript:saveSvgFromParentDiv('svgWrapper14','Intensity distribution accross peptides.svg');\" >Save figure</a></div>"))
  invisible(dev.off())
  
  cat(text_spec(paste0("Intensities were normalized by computing the ratio beetween each acquired intensity and the intensity of the first acquired time where all precursors were observed (",ref_data$AcquiredTime[1],")"), italic=T, font_size="12px"))
  
}else{
  cat(text_spec("No acquired time at which one all precursors were observed was found."))
}

```


<br>
<div id="banner">
# PPM
</div>
<br>

```{r extract_PPM}

PPM = substring(input$Annotations, regexpr("delta PPM = ", input$Annotations) + 12)
input$PPM = as.numeric(PPM)

```

```{r median_centering_ppm, results='asis'}
# Median computing for each AcquiredTime
input = input[order(as.Date(input$AcquiredTime)),]
ppm_median = c()
for (date in unique(input$AcquiredTime)){
  sub = subset(input, input$AcquiredTime==date)
  median = median(sub$PPM)
  ppm_median = c(ppm_median,median)
}

gg1 = ggplot() +
  geom_line(data = input, aes(x = AcquiredTime, y = PPM,group=as.factor(input$Precursor), colour = Precursors),size=0.8)+
  geom_line(aes(x= unique(input$AcquiredTime),y=ppm_median,group=1,linetype="median"),col="black",size=0.8)+
  ggtitle("PPM deviation")+
  ylab("Centered PPM") +
  theme(axis.text.x=element_text(angle=90,size=12),
        axis.text.y=element_text(size=22),
        plot.title=element_text(size=28),
        legend.text=element_text(size=20),
        legend.title = element_text(size=22),
        axis.title=element_text(size=22))

s <- svgstring(width=20,height=10)
plot(gg1)
htmltools::HTML("<div id=\"svgWrapper15\" ",s(),"<a class='no-print' href=\"javascript:saveSvgFromParentDiv('svgWrapper15','PPM deviation.svg');\" >Save figure</a></div>")
invisible(dev.off())

cat(text_spec("\n"))

gg2 = ggplot() +
  geom_boxplot(data = input, aes(x = Precursor, y = PPM, col = Precursors),size=0.8)+
  geom_boxplot(aes(x="1",y=ppm_median,linetype="median"),size=0.8)+
  ggtitle("PPM distribution accross peptides")+
  ylab("PPM")+
  xlab("")+
  theme(axis.text.x = element_blank(),
        axis.text.y=element_text(size=22),
        plot.title=element_text(size=28),
        legend.text=element_text(size=20),
        legend.title = element_text(size=22),
        axis.title=element_text(size=22))

s <- svgstring(width=20,height=10)
plot(gg2)
htmltools::HTML("<div id=\"svgWrapper16\" ",s(),"<a class='no-print' href=\"javascript:saveSvgFromParentDiv('svgWrapper16','PPM distribution accross peptides.svg');\" >Save figure</a></div>")
invisible(dev.off())

```

<br>
<div id="banner">
# Metrics deviation by precursor
</div>
<br>

```{r opts.label="kill_prefix", results='asis'}

colour = unique(ggplot_build(gg1)$data[[1]]$colour)
input$Precursors = paste0(input$Precursor," (",input$mz,")")

i=1

for (peptide in unique(input$Precursors)){
  sub = subset(input, input$Precursors==peptide)
  peptide_name = unique(sub$Precursor)
  
gg1 =   ggplot(data = sub) +
  geom_line(aes(x = AcquiredTime, y = TotalArea,group=1),col=colour[i],show.legend = F,size=0.8)+
  ggtitle(paste0("Absolute intensity deviation of ",peptide_name))+
  ylab("Intensity")+
   theme(axis.text.x=element_text(angle=90,size=18),
         axis.text.y=element_text(size=22),
         plot.title=element_text(size=28),
         legend.text=element_text(size=20),
         legend.title = element_text(size=22),
         axis.title=element_text(size=22))

gg2 =   ggplot(data = sub) +
  geom_line(aes(x = AcquiredTime, y = Best.RT,group=1),col=colour[i],show.legend = F,size=0.8)+
  ggtitle(paste0("Absolute RT deviation of ",peptide_name))+
  ylab("RT")+
  theme(axis.text.x=element_text(angle=90,size=18),
        axis.text.y=element_text(size=22),
        plot.title=element_text(size=28),
        legend.text=element_text(size=20),
        legend.title = element_text(size=22),
        axis.title=element_text(size=22))

gg3 =  ggplot(data = sub) +
  geom_line(aes(x = AcquiredTime, y = sub$PPM,group=1),col=colour[i],show.legend = F,size=0.8)+
  ggtitle(paste0("Absolute PPM deviation of ",peptide_name))+
  ylab("PPM")+
  theme(axis.text.x=element_text(angle=90,size=18),
        axis.text.y=element_text(size=22),
        plot.title=element_text(size=28),
        legend.text=element_text(size=20),
        legend.title = element_text(size=22),
        axis.title=element_text(size=22))

  cat(text_spec(peptide, color=as.character(colour[i]), bold=T, font_size=18 ))
  
  s <- svgstring(width=20,height=10)
  plot(gg1)
  cat(htmltools::HTML("<div id=\"svgWrapper17\" ",s(),"<a class='no-print' href=\"javascript:saveSvgFromParentDiv('svgWrapper17','PPM distribution accross   peptides.svg');\" >Save figure</a></div>"))
  invisible(dev.off())

  s <- svgstring(width=20,height=10)
  plot(gg2)
  cat(htmltools::HTML("<div id=\"svgWrapper17\" ",s(),"<a class='no-print' href=\"javascript:saveSvgFromParentDiv('svgWrapper17','PPM distribution accross   peptides.svg');\" >Save figure</a></div>"))
  invisible(dev.off())
  
  s <- svgstring(width=20,height=10)
  plot(gg3)
  cat(htmltools::HTML("<div id=\"svgWrapper17\" ",s(),"<a class='no-print' href=\"javascript:saveSvgFromParentDiv('svgWrapper17','PPM distribution accross   peptides.svg');\" >Save figure</a></div>"))
  invisible(dev.off())
  
  i=i+1
}

```

